### 2003-02-06 papers/hypertext2003/paper.tex
Added paper skeleton and some bib entries.

%
% Modification History
%
% 2003-February-6  Jason Rohrer
% Created.
%

\documentclass{acm_proc_article-sp}

\begin{document}

\title{token\_word:  Building a Xanalogical System in Nine Days}

\numberofauthors{1}

\author{
\alignauthor Jason Rohrer\\
    \affaddr{University of California, Santa Cruz}\\
    \affaddr{Dept. of Computer Science}\\
    \affaddr{Santa Cruz, CA 95064}\\
    \email{rohrer@cse.ucsc.edu}
}

\date{February 6, 2003}

\maketitle

\begin{abstract}
Test

\end{abstract}

\category{H.5.4}{Information Interfaces and Applications}{Hypertext/Hypermedia}[Architectures]
\category{K.4}{Computers and Society}{Electronic Commerce}[Payment Schemes]

\terms{Design, Human Factors}

\keywords{Micropayments, quotation, transclusion, Xanadu}

\section{Introduction}

\cite{NelsonLiteraryMachines}

\section{System Architecture}

\subsection{Xanalogical Improvements}

\section{Implementation}

\section{Micropayment Issues}

\subsection{Balancing Risk}

\section{Related work}

Wikis
\cite{WikiWikiWeb}
\cite{Wikipedia}

Everything2
\cite{Everything2}

Weblogs
\cite{kuro5hin}

Xanadu

\section{Conclusion}

\section{Acknowledgements}
Thanks are due to Ted Nelson and Jim Whitehead for their contributions to interesting Xanalogical discussions over the past year.

\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}

### 2003-02-06 papers/hypertext2003/paper.tex
Added an introduction and a section about Xanadu.

@@
 
+\newcommand{\tw}{token\_word}
+
 \begin{document}
 
-\title{token\_word:  Building a Xanalogical System in Nine Days}
+\title{\tw:  Building a Xanalogical System in Nine Days}
 
@@
 \begin{abstract}
-Test
+We describe \tw, a web-based xanalogical hypertext system.  Our system supports almost every feature associated with Xanadu, an architecture that has been actively discussed for nearly forty years.
+Features include deep quotation, unbreakable references, two-way reference chasing, and frictionless micropayments backed by real-world currency.
+To our knowledge, \tw \ is the first xanalogical system implementation to included all of these features.
+Also, \tw \ is the first xanalogical system of any kind to be accessible through a web browser with no additional software.
+
+Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \ was implented from scratch in nine days by one person.  
+We attribute this success to the maturity of modern technology and design techniques.  
+In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
 
@@
 \section{Introduction}
+Xanadu has been floating in the collective mind of the hypertext research community for nearly forty years.
+Xanadu is a dream and an ideal.  
+We know it would be great (or at least interesting) if a xanalogical system existed, but we are also resigned to the notion that such a system will probably never exist.
+Is Xanadu impossible?
 
-\cite{NelsonLiteraryMachines}
+That question by itself, the impossibility question, is extraordinarily intriguing.  We {\it know} that Xanadu is not impossible.  
+The design, on paper, is clear enough:  we just need to build it.  
+The problem might be that no one tried to build it.  
+But many people did try to build Xanadu over the years.  
+The problem might be that the people trying to build it did not have sufficient resources.  But people with extraordinary resources did try to build it.  
+Will anyone argue that Autodesk did not have extraordinary software development resources in the late 1980s?  
+Furthermore, Autodesk {\it believed} in Xanadu.  
+The following quote from a 1988 Autodesk press release is most telling:
+
+\begin{quote}
+In 1964, Xanadu was a dream in a single mind.  In 1980, it was the
+shared goal of a small group of brilliant technologists.  By 1989, it
+will be a product.  And by 1995 it will begin to change the world.
+Much work remains to be done to realise the potential of Xanadu--it
+will take the Xanadu development team 18 months to field the first
+Xanadu system. \cite{AutodeskPress} 
+\end{quote}
+
+In that same press release, Autodesk claims 1987 sales figures topping \$79 million.  
+Indeed, Autodesk had extraordinary resources for its time.  
+In 1992, after four years of development and \$5 million spent \cite{AutodeskCost},  Autodesk ceased development of Xanadu \cite{AutodeskPressDrop}.  
+Ironically, this decision was made just when the world was ripe for its first global hypertext system \cite{BernersLee92}.
+
+We are scared of Xanadu.  
+We hear its siren song and are tempted, but we know that many have tried and many have failed.  
+The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
+We can look at architecture drawings and pictures of cardboard mock-ups\cite{Nelson1999}, but these do not give us any sense of what it would be like to use a xanalogical system.  
+Few of us have ever played with a xanalogical software prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
+
+What is using a xanalogical system really like?
+Is it as useful as it sounds?  
+This paper attempts to answer this question by describing the first fully-realized xanalogical implementation.
+
+\section{The Xanadu Model}
+
+As mentioned in the above quote, Xanadu's underlying ideas were first incubated by Nelson in the 1960s \cite{Nelson1965}.  
+These ideas evolved somewhat over the next forty years, receiving one of their most verbose presentations in Nelson's book {\it Literary Machines}, which was first published in 1981 \cite{NelsonLiteraryMachines}.
+Nelson's more recent paper on the xanalogical model is up to date in terms of modern technological trends, but the core ideas have not changed \cite{Nelson1999}.  
+The high-level description and interpretation of Xanadu given here is based on information culled from {\it Literary Machines}, Nelson's recent lectures, and personal conversations with Nelson.
+
+The goal of Xanadu, distilled into a single phrase, is {\it frictionless content reuse}.  
+This goal would be easily realized in a frictionless, copyright-free world:  authors could simply copy whatever they want and reuse it however they want.  
+In our world, however, we have copyright.
+Unlike other systems \cite{Clark2000}, Xanadu does not attempt to undermine copyright, but instead tries to work with it. 
+All of the design choices and complications in the Xanadu model can be seen as mechanisms for making reuse frictionless in the face of copyright.
+When trying to implement unrestricted reuse in a way that works with copyright, we are faced with the following fact:  {\it copyright forbids unrestricted copying}.
+
+Xanadu's central mechanism is {\it transclusion}, a form of quotation.  
+Transclusion differs from quotation in that it does not involve copying of any kind.  
+When document $A$ transcludes a quote from document $B$ the quote is stored as a deep reference to the quoted material in $B$:  words from $B$ are not copied into $A$. 
+Whenver $A$ is viewed, the words from $A$ are fetched from $A$'s owner, and the necessary word from $B$ are fetched from $B$'s owner.
+Thus, even though $A$'s owner has quoted document $B$, the quoted owner still retains control over his or her words.
+Avoiding copying led us to transclusion, and making transclusion work will lead us to the rest of the Xanadu model.
+
+Transclusion creates a serious problem, at least in combination with how we commonly think of electronic documents.
+Electronic documents change constantly.
+If $B$ changes or is deleted, $A$'s quote can break.
+Xanadu's solution is to forbid document change but encourage document versioning.
+Thus, as $B$ changes, all previous versions are maintained, and $A$'s quote can point to the particular version that $A$'s owner quoted.
+A particular version of $B$ is immutable, so $A$'s quote will never break.
+
+The Xanadu model refines this versioning model further by describing an ever-growing, add-only, content space.  
+When a document is created, its text is added to this space.
+When a document quotes this document, it points not to the document itself, but to the quoted words in the content space.
+Thus, a document in Xanadu is a series of pointers to regions in the content space, and no text is contained in the documents themselves.
+Versioning with this mechanism is particularly space-efficient:  unchanged portions of the document can be quoted from the content space instead of being duplicated.
 
@@
 \subsection{Xanalogical Improvements}
+
+\subsection{Missing Features}
 
@@
 \section{Acknowledgements}
-Thanks are due to Ted Nelson and Jim Whitehead for their contributions to interesting Xanalogical discussions over the past year.
+Thanks are due to Ted Nelson and Jim Whitehead for their contributions to interesting xanalogical discussions over the past year.
+``Xanadu'' is a trademark of Ted Nelson.
+To prevent confusion, the generic terms ({\it e.g.}, xanalogical) have been used wherever possible.
 

### 2003-02-07 papers/hypertext2003/paper.tex
Finished Xanadu section, and started on System Architecture section.

@@
 That question by itself, the impossibility question, is extraordinarily intriguing.  We {\it know} that Xanadu is not impossible.  
-The design, on paper, is clear enough:  we just need to build it.  
+The design, on paper \cite{NelsonLiteraryMachines}, is clear enough:  we just need to build it.  
 The problem might be that no one tried to build it.  
@@
 will be a product.  And by 1995 it will begin to change the world.
-Much work remains to be done to realise the potential of Xanadu--it
+Much work remains to be done to realise the potential of Xanadu---it
 will take the Xanadu development team 18 months to field the first
@@
 
-In that same press release, Autodesk claims 1987 sales figures topping \$79 million.  
+In the same press release, Autodesk claims 1987 sales figures topping \$79 million.  
 Indeed, Autodesk had extraordinary resources for its time.  
@@
 The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
-We can look at architecture drawings and pictures of cardboard mock-ups\cite{Nelson1999}, but these do not give us any sense of what it would be like to use a xanalogical system.  
+We can look at architecture drawings and pictures of cardboard mock-ups \cite{Nelson1999}, but these do not give us any sense of what it would be like to use a xanalogical system.  
 Few of us have ever played with a xanalogical software prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
@@
 Is it as useful as it sounds?
-This paper attempts to answer this question by describing the first fully-realized xanalogical implementation.
+What made implementing Xanadu so difficult for so many people?  
+This paper attempts to answer these question by describing the first fully-realized xanalogical implementation.
 
@@
 Transclusion differs from quotation in that it does not involve copying of any kind.  
-When document $A$ transcludes a quote from document $B$ the quote is stored as a deep reference to the quoted material in $B$:  words from $B$ are not copied into $A$. 
-Whenver $A$ is viewed, the words from $A$ are fetched from $A$'s owner, and the necessary word from $B$ are fetched from $B$'s owner.
-Thus, even though $A$'s owner has quoted document $B$, the quoted owner still retains control over his or her words.
-Avoiding copying led us to transclusion, and making transclusion work will lead us to the rest of the Xanadu model.
+When document $A$ transcludes a quote from document $B$, the quote is stored as a deep reference to the quoted material in $B$:  words from $B$ are not copied into $A$. 
+Whenver $A$ is viewed, the words from $A$ are fetched from $A$'s owner, and the necessary words from $B$ are fetched from $B$'s owner.
+Thus, even though $A$'s owner has quoted document $B$, the quoted owner still retains control over the distribution and licensing of his or her words.
+%Avoiding copying led us to transclusion, and making transclusion work will lead us to the rest of the Xanadu model.
 
-Transclusion creates a serious problem, at least in combination with how we commonly think of electronic documents.
+Transclusion creates a serious problem, at least in combination with how we commonly interact with electronic documents.
 Electronic documents change constantly.
@@
 
-The Xanadu model refines this versioning model further by describing an ever-growing, add-only, content space.  
+The Xanadu model refines versioning further by describing an ever-growing, add-only, content space.  
 When a document is created, its text is added to this space.
-When a document quotes this document, it points not to the document itself, but to the quoted words in the content space.
-Thus, a document in Xanadu is a series of pointers to regions in the content space, and no text is contained in the documents themselves.
-Versioning with this mechanism is particularly space-efficient:  unchanged portions of the document can be quoted from the content space instead of being duplicated.
+When a document quotes another document, it points not to the document itself, but to the quoted words in the content space.
+Thus, a document in Xanadu is a series of pointers to regions in the content space---no text is contained in the documents themselves.
+Versioning with this mechanism is particularly space-efficient:  unchanged portions of a document can be quoted from the content space instead of being duplicated.
+
+Along with complicating document maintenance, transclusion complicates the licensing of copyrighted material.
+We commonly think about licensing documents only in their entirety.
+For example, we may assign monetary value to the printed copy of a book, but we have difficulty imagining how much a chapter, page, or paragraph of that book is worth.
+In the Xanadu model, when users read a quote from document $B$ embedded in document $A$, they may only be accessing a small portion of $B$ (for example, a single sentence from a 10,000-word document).
+Thus, $B$'s owner must be prepared to license only a portion of $B$ to readers.
+The Xanadu model handles this licensing issue with micropayments and per-character values for content.
+Nelson is fond of using the word {\it nanobuck} ($10^{-9}$ dollars) to describe the smallest unit of payment:  documents, or portions of documents, are licensed for $N$ nanobucks per character.
+For example, if $N=100$, a document containing one million characters, if licensed in its entirety, would cost \$0.10, while the first half would cost only \$0.05.
+
+When licensing a portion of a document in the Xanadu model, users are actually licensing a region of the content space.
+Each character in the content space can be acquired for a one-time licensing fee.
+Thus, if users purchase documents that overlap with regions they already own, they only pay for the portions that they have yet to acquire.
+Each user accumulates a ``library'' of acquired text regions over time and pays for each region only once.
+
+When a document is accessed that contains quotes from multiple authors, the micropayments are divided and routed to the original authors on a per-character basis. 
+Though reading content requires payment, quoting is essentially free, since the content is not accessed during the act of quoting.
+Of course, in practice, an author will need to read a document before quoting it, but this reading requires the normal first-access payment, no matter how widely the new document is expected to be read.
+In fact, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
+Thus, authors benefit from the unrestricted quotation and reuse of their work:  they have no financial motivation for placing limits on their work.
+
+We can summarize the Xanadu model with the following feature list:  deep quotation by reference; static underlying content; and per-character, one-time micropayments.
 
 \section{System Architecture}
+We built \tw, a full-featured xanalogical system, from scratch in only nine days.
+To acheive this kind rapid development, we relied heavily on modern technology and design techniques.
+We do not view past Xanadu failures with disdain.
+We acknowledge that those early attempts were too far ahead of their time:  the technology of the day was simly not ready for Xanadu.
+The central technologies that made \tw \  development possible were the web, CGI, and Perl.
+
+Our system, though full-featured, was not designed to be ``the'' scalable xanalogical system that will carry us all into the future.
+Instead, we focused on building a usable implemenation of xanalogical features for the purpose of experimentation.
+Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other projects.
 

### 2003-02-07 papers/hypertext2003/paper.tex
Added images and discussed implementation.

@@
 In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
-
+A live \tw \ system is running at
+\begin{center}
+http://hypertext.sf.net/token\_word
+\end{center}
 \end{abstract}
@@
 \section{System Architecture}
-We built \tw, a full-featured xanalogical system, from scratch in only nine days.
+We designed and built \tw, a full-featured xanalogical system, from scratch in only nine days.
 To acheive this kind rapid development, we relied heavily on modern technology and design techniques.
 We do not view past Xanadu failures with disdain.
-We acknowledge that those early attempts were too far ahead of their time:  the technology of the day was simly not ready for Xanadu.
-The central technologies that made \tw \  development possible were the web, CGI, and Perl.
+We acknowledge that those early attempts were simply ahead of their time:  the technology of the day was not ready for Xanadu.
+The central technologies that made \tw \  development possible were the web, CGI, Perl, and PayPal \cite{paypal}.
 
@@
 Instead, we focused on building a usable implemenation of xanalogical features for the purpose of experimentation.
-Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other projects.
+Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other web-based projects \cite{Everything2}.
+
+\subsection{User Perspective}
+From the end-user's perspective, \tw \ has several sal\-ient features.
+Users access \tw \ with a web browser, and they must create accounts and log in to use the system.  
+The central elements of the system are documents, which can contain quotes of other documents.
+Quote markers can be hidden or displayed, and a quote can be followed to see the context from which it was taken.
+Each document also features a list of documents that quote it.
+The \tw \  document display interface can be seen in Figure \ref{fig:mainScreen}.
+
+\begin{figure}[t]
+\label{fig:mainScreen}
+\centering
+\epsfig{file=images/mainScreen.eps, width=20pc}
+\caption{The document display interface.}
+\end{figure}
+
+Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
+Quotes on a clipboard can be followed to see quote context.
+The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
+When creating a new document, a user can enter new text along with references to quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
+A preview mode shows the new document with all quote reference expanded, as seen in Figure \ref{fig:docPreview}.
+
+\begin{figure}[t]
+\label{fig:quoteClipboard}
+\centering
+\epsfig{file=images/quoteClipboard.eps, width=20pc}
+\caption{The quote clipboard interface.}
+\end{figure}
+
+Each user has a token balance, where one token is worth one character.
+The current exchange rate is 1,000,000 tokens for \$1, and Paypal is integrated for token deposits and withdrawls.
+Viewing a document that contains as of yet unviewed text transfers tokens from the reader to the authors of the unviewed text.
+Users only pay for each piece of text once---repeat viewings of the same text, in any context, are free.
+\begin{figure}[t]
+\label{fig:docCreate}
+\centering
+\epsfig{file=images/docCreate.eps, width=20pc}
+\caption{The document creation interface. Quote 1 from the clipboard is used.}
+\end{figure}
+
+\begin{figure}[t]
+\label{fig:docPreview}
+\centering
+\epsfig{file=images/docPreview.eps, width=20pc}
+\caption{The document preview interface.  Quotes are expanded, and possible spelling mistakes are highlighed.}
+\end{figure}
+
+Full text searches are supported across the entire document database, and search terms are highlighted when result documents are displayed.
+Search results (and other lists in \tw) are sorted with most-quoted documents first, since frequently quoted documents are likely to contain the best information.
+
+\tw \ does provides no explicit linking mechanism.
+However, since quote context can be obtained easily, brief quotes can be used as links between documents.
+For an example of quotes used to link, see Figure \ref{fig:quotesAsLinks}.
+
+\begin{figure}[t]
+\label{fig:quotesAsLinks}
+\centering
+\epsfig{file=images/quotesAsLinks.eps, width=20pc}
+\caption{Brief portions of documents can be quoted to form links.}
+\end{figure}
+
+\subsection{Implementation Details}
+
+Keeping with the Xanadu model, \tw \ separates documents from the text they contain.
+There are two types of data objects in \tw:  documents and chunks.
+A chunk contains a raw block of contiguous text, while a document is a list of reference to text chunks.
+Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.
+Quote clipboards, like documents, contain a list of references.
+However, to support showing the context of a quote, the references are not to chunks, but to the context documents themselves.
+The chunks associated with a quote are only resolved when the quote is used as part of a new document.
+
+\subsubsection{Development}
+The entire \tw \  system is implemented as a single CGI script written in Perl.
+Perl's built-in support for regular expressions was very useful for the rather complicated text processing done by \tw.
+Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
+For example, highlighting of possible misspellings in preview mode was a minor addition that required less than ten lines of code.
+
+CGI programming is well-supported in Perl, and HTML may user interface layout and user action processing easy to implement.
+
+\subsubsection{Data Representation}
+The system data is stored in a directory tree on the filesystem.
+Each user has directory that stores that user's chunk files, document files, and quote clipboard files, along with a list of previously purchased chunk regions.
+To support two-way reference chasing, each document has a file that tracks the documents that quote it.
+
+References throughout the system are stored in the following form:
+\begin{center}
+{\tt <chunkUserID, chunkID, startOffset, length;\\ 
+docUserID, docID, startOffset>} 
+\end{center}
+The portion of the reference befor the ``;'' describes the text chunk of the reference.  
+The second portion, which is optional, describes the quote context of the reference.  
+Note that {\tt chunkUserID} may differ from {\tt docUserID}, since the quote context may be part of a quote in another document.
+For example, document $A$ may quote from document $B$, but the portion that $A$ quotes may be part of $B$'s quote from document $C$.
+In this example, the reference included in $A$ might look like this:
+\begin{center}
+{\tt <userC, C, 105, 38; userB, B, 421>} 
+\end{center}
+Note that {\tt length} is not specified for the document context of a reference, since it would be redundant.
+
+Thus, a reference can be used both to fetch the required text chunk region and to display context in case of a followed quote reference.
+By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
+When a new chunk is created as part of a document, the context portion of the reference is ommited.
+
+Since documents and text chunks are static, full text searches can be implemented using an index that is updated in real time as documents are created.
+Each word in the index is associated with a list of documents containing that word.
+When a document is added to the system, it is appended to the end of the index list for each word that it contains.
+
+\subsubsection{Implementation Limitations}
+The main limitation of our implementation is the use of a filesystem as a data backend.
 
@@
 \subsection{Missing Features}
-
-\section{Implementation}
 

### 2003-02-07 papers/hypertext2003/paper.tex
Added Opera window size for taking screen shots.
Proofread a bit, improved wording, added new image, and re-cropped images.

@@
 We describe \tw, a web-based xanalogical hypertext system.  Our system supports almost every feature associated with Xanadu, an architecture that has been actively discussed for nearly forty years.
-Features include deep quotation, unbreakable references, two-way reference chasing, and frictionless micropayments backed by real-world currency.
+Features include deep quotation, unbreakable references, two-way reference chasing, and frictionless micropayments that are backed by real-world currency.
 To our knowledge, \tw \ is the first xanalogical system implementation to included all of these features.
-Also, \tw \ is the first xanalogical system of any kind to be accessible through a web browser with no additional software.
+Furthermore, \tw \ is the first xanalogical system of any kind to be accessible by a web browser with no additional software.
 
@@
 In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
-A live \tw \ system is running at
+A live \tw \ system is running at:
 \begin{center}
@@
 
-In the same press release, Autodesk claims 1987 sales figures topping \$79 million.  
+In the same press release, Autodesk claimed 1987 sales figures topping \$79 million.  
 Indeed, Autodesk had extraordinary resources for its time.  
 In 1992, after four years of development and \$5 million spent \cite{AutodeskCost},  Autodesk ceased development of Xanadu \cite{AutodeskPressDrop}.  
-Ironically, this decision was made just when the world was ripe for its first global hypertext system \cite{BernersLee92}.
+Ironically, this decision was made just when the world was ripe for the first global hypertext system \cite{BernersLee92}.
 
@@
 The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
-We can look at architecture drawings and pictures of cardboard mock-ups \cite{Nelson1999}, but these do not give us any sense of what it would be like to use a xanalogical system.  
-Few of us have ever played with a xanalogical software prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
+We can look at architecture drawings and pictures of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
+Few of us have ever played with a xanalogical user interface prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
 
@@
 This paper attempts to answer these question by describing the first fully-realized xanalogical implementation.
+
+Given this historical perspective, the contributions of this paper are threefold.
+First, this paper analyzes the process that lead from a paper design to real world xanalogical software.
+Second, this paper shows that modern technology and techniques are of utmost importance for making this implementation process {\it possible}, let alone quick.
+Third, this paper describes a full xanalogical system implementation from the perspective of an end-user.
+The novelty of this paper hinges on the implmentation, which has a modern flavor, though the underlying ideas are quite old.
+We have acheived a novel success, where past attempts have failed, and we feel that the lessons learned from this process are valuable.
 
@@
 
-The goal of Xanadu, distilled into a single phrase, is {\it frictionless content reuse}.  
-This goal would be easily realized in a frictionless, copyright-free world:  authors could simply copy whatever they want and reuse it however they want.  
+The chief goal of Xanadu, distilled into a single phrase, is {\it frictionless content reuse}.  
+This goal would be easily realized in a frictionless, copyright-free world:  authors could simply copy whatever they want and reuse it however they please.  
 In our world, however, we have copyright.
@@
 All of the design choices and complications in the Xanadu model can be seen as mechanisms for making reuse frictionless in the face of copyright.
-When trying to implement unrestricted reuse in a way that works with copyright, we are faced with the following fact:  {\it copyright forbids unrestricted copying}.
+When trying to implement unrestricted reuse in a way that works with copyright, we are faced with the following issue:  {\it copyright forbids unrestricted copying}.
 
@@
 When a document quotes another document, it points not to the document itself, but to the quoted words in the content space.
-Thus, a document in Xanadu is a series of pointers to regions in the content space---no text is contained in the documents themselves.
-Versioning with this mechanism is particularly space-efficient:  unchanged portions of a document can be quoted from the content space instead of being duplicated.
+Thus, a document in Xanadu is a list of pointers to regions in the content space---no text is contained in the documents themselves.
+Versioning with this mechanism is particularly space-efficient:  unchanged portions of a new document version can be quoted from the content space instead of being duplicated.
 
@@
 We commonly think about licensing documents only in their entirety.
-For example, we may assign monetary value to the printed copy of a book, but we have difficulty imagining how much a chapter, page, or paragraph of that book is worth.
+For example, we may assign monetary value to a printed copy of a book, but we have difficulty imagining how much a chapter, page, or paragraph of that book is worth.
 In the Xanadu model, when users read a quote from document $B$ embedded in document $A$, they may only be accessing a small portion of $B$ (for example, a single sentence from a 10,000-word document).
@@
 The Xanadu model handles this licensing issue with micropayments and per-character values for content.
-Nelson is fond of using the word {\it nanobuck} ($10^{-9}$ dollars) to describe the smallest unit of payment:  documents, or portions of documents, are licensed for $N$ nanobucks per character.
+Nelson is fond of using the term {\it nanobuck} ($10^{-9}$ dollars) to describe the smallest unit of payment:  documents, or portions of documents, are licensed for $N$ nanobucks per character.
 For example, if $N=100$, a document containing one million characters, if licensed in its entirety, would cost \$0.10, while the first half would cost only \$0.05.
@@
 When licensing a portion of a document in the Xanadu model, users are actually licensing a region of the content space.
-Each character in the content space can be acquired for a one-time licensing fee.
+Each character in the content space can be permanently acquired for a one-time licensing fee.
 Thus, if users purchase documents that overlap with regions they already own, they only pay for the portions that they have yet to acquire.
@@
 Though reading content requires payment, quoting is essentially free, since the content is not accessed during the act of quoting.
-Of course, in practice, an author will need to read a document before quoting it, but this reading requires the normal first-access payment, no matter how widely the new document is expected to be read.
+In practice, an author will need to read a document before quoting it, but this reading requires the normal first-access payment, no matter how widely the new document is expected to be read.
 In fact, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
-Thus, authors benefit from the unrestricted quotation and reuse of their work:  they have no financial motivation for placing limits on their work.
+Thus, authors benefit from the unrestricted quotation and reuse of their work:  they have no financial motivation for imposing any limits.
 
@@
 We designed and built \tw, a full-featured xanalogical system, from scratch in only nine days.
-To acheive this kind rapid development, we relied heavily on modern technology and design techniques.
+To acheive this kind of rapid development, we relied heavily on modern technology and design techniques.
 We do not view past Xanadu failures with disdain.
-We acknowledge that those early attempts were simply ahead of their time:  the technology of the day was not ready for Xanadu.
+Those early attempts were simply ahead of their time:  the technology of the day was not ready for Xanadu.
 The central technologies that made \tw \  development possible were the web, CGI, Perl, and PayPal \cite{paypal}.
@@
 Instead, we focused on building a usable implemenation of xanalogical features for the purpose of experimentation.
-Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other web-based projects \cite{Everything2}.
+Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
 
 \subsection{User Perspective}
-From the end-user's perspective, \tw \ has several sal\-ient features.
+In describing the \tw \ user experience, we are faced with the very issue that motivated \tw \ development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to {\it use} a system.
+Since this paper's focus is on a real-world implementation and not just a paper description, we encourage readers to visit {\tt http://hypertext.sf.net/token\_word} to try our system for themselves.
+
+From the end-user's perspective, \tw \ has many sal\-ient features.
 Users access \tw \ with a web browser, and they must create accounts and log in to use the system.  
@@
 
+% opera window size for figures:
+% 737 x 528
 \begin{figure}[t]
-\label{fig:mainScreen}
 \centering
@@
 \caption{The document display interface.}
+\label{fig:mainScreen}
 \end{figure}
@@
 Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
+Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
 Quotes on a clipboard can be followed to see quote context.
@@
 When creating a new document, a user can enter new text along with references to quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
-A preview mode shows the new document with all quote reference expanded, as seen in Figure \ref{fig:docPreview}.
+A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.
 
 \begin{figure}[t]
-\label{fig:quoteClipboard}
+\centering
+\epsfig{file=images/extractQuote.eps, width=20pc}
+\caption{The interface for extracting a quote.  The region surrounded by $<$q$>$ $<$$/$q$>$ tags is selected for extraction.}
+\label{fig:extractQuote}
+\end{figure}
+
+\begin{figure}[t]
 \centering
@@
 \caption{The quote clipboard interface.}
+\label{fig:quoteClipboard}
 \end{figure}
@@
 The current exchange rate is 1,000,000 tokens for \$1, and Paypal is integrated for token deposits and withdrawls.
-Viewing a document that contains as of yet unviewed text transfers tokens from the reader to the authors of the unviewed text.
+When a reader views a document that contains as of yet unviewed text regions, tokens are transfered from the reader to the original authors of the regions.
 Users only pay for each piece of text once---repeat viewings of the same text, in any context, are free.
 \begin{figure}[t]
-\label{fig:docCreate}
 \centering
 \epsfig{file=images/docCreate.eps, width=20pc}
-\caption{The document creation interface. Quote 1 from the clipboard is used.}
+\caption{The document creation interface. Quote 1 from the clipboard is inserted with the $<$q1$>$ tag.}
+\label{fig:docCreate}
 \end{figure}
@@
 \begin{figure}[t]
-\label{fig:docPreview}
 \centering
@@
 \caption{The document preview interface.  Quotes are expanded, and possible spelling mistakes are highlighed.}
+\label{fig:docPreview}
 \end{figure}
@@
 
-\tw \ does provides no explicit linking mechanism.
+\tw \ provides no explicit linking mechanism.
 However, since quote context can be obtained easily, brief quotes can be used as links between documents.
@@
 \begin{figure}[t]
-\label{fig:quotesAsLinks}
 \centering
@@
 \caption{Brief portions of documents can be quoted to form links.}
+\label{fig:quotesAsLinks}
 \end{figure}

### 2003-02-07 papers/hypertext2003/paper.tex
Fixed more wording.

@@
 The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
-We can look at architecture drawings and pictures of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
+We can look at architecture diagrams and photgraphs of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
 Few of us have ever played with a xanalogical user interface prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
@@
 Xanadu's central mechanism is {\it transclusion}, a form of quotation.  
-Transclusion differs from quotation in that it does not involve copying of any kind.  
+Transclusion differs from standard quotation in that it does not involve copying of any kind.  
 When document $A$ transcludes a quote from document $B$, the quote is stored as a deep reference to the quoted material in $B$:  words from $B$ are not copied into $A$. 
@@
 Xanadu's solution is to forbid document change but encourage document versioning.
-Thus, as $B$ changes, all previous versions are maintained, and $A$'s quote can point to the particular version that $A$'s owner quoted.
+Thus, as $B$ is updated, all previous versions are maintained, and $A$'s quote can point to the particular version that $A$'s owner quoted.
 A particular version of $B$ is immutable, so $A$'s quote will never break.
@@
 When a document is created, its text is added to this space.
-When a document quotes another document, it points not to the document itself, but to the quoted words in the content space.
+When a document transcludes from another document, it points not to the document itself, but to the transcluded words in the content space.
 Thus, a document in Xanadu is a list of pointers to regions in the content space---no text is contained in the documents themselves.
-Versioning with this mechanism is particularly space-efficient:  unchanged portions of a new document version can be quoted from the content space instead of being duplicated.
+Versioning with this mechanism is particularly space-efficient:  unchanged portions of a new document version can be transcluded from the content space instead of being duplicated.
 
-Along with complicating document maintenance, transclusion complicates the licensing of copyrighted material.
+Along with requiring a new model for document maintenance, transclusion pushes us toward a new model for licensing copyrighted material.
 We commonly think about licensing documents only in their entirety.
@@
 Though reading content requires payment, quoting is essentially free, since the content is not accessed during the act of quoting.
-In practice, an author will need to read a document before quoting it, but this reading requires the normal first-access payment, no matter how widely the new document is expected to be read.
+In practice, an author will need to read a document before quoting it, but this reading requires only the normal first-access payment, no matter how widely the new, quoting document is expected to be read.
 In fact, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
@@
 Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
+We claim that \tw \  could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.
 
@@
 The central elements of the system are documents, which can contain quotes of other documents.
-Quote markers can be hidden or displayed, and a quote can be followed to see the context from which it was taken.
-Each document also features a list of documents that quote it.
+Quote markers can be hidden or displayed, and quotes can be followed to see the context from which they were taken.
+Each document also features a list of documents that quote it, so references can be chased in both directions.
 The \tw \  document display interface can be seen in Figure \ref{fig:mainScreen}.
@@
 \subsubsection{Development}
-The entire \tw \  system is implemented as a single CGI script written in Perl.
+The entire \tw \  system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
 Perl's built-in support for regular expressions was very useful for the rather complicated text processing done by \tw.
 Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
-For example, highlighting of possible misspellings in preview mode was a minor addition that required less than ten lines of code.
+For example, highlighting possible misspellings in preview mode was a minor addition that required less than ten lines of code.
 
-CGI programming is well-supported in Perl, and HTML may user interface layout and user action processing easy to implement.
+CGI programming is well-supported in Perl, and HTML made user interface layout and user action processing easy to implement.
+Perl-based CGI programming seems to be the modern method of choice for rapidly developing complex, multi-user applications.
+Other systems that have used this development method successfully are discussed in Section \ref{sec:RelatedWork}.
 
@@
 
-Thus, a reference can be used both to fetch the required text chunk region and to display context in case of a followed quote reference.
+With this representation, a reference can be used both to fetch the required text chunk region and to display context in case of a followed quote reference.
 By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
-When a new chunk is created as part of a document, the context portion of the reference is ommited.
+When a new chunk is created as part of a document, the context portion of the reference is ommited, indicating that the document is the first context in which this chunk was used.
 
@@
 
-\section{Related work}
+\section{Related Work}
+\label{sec:RelatedWork}
 

### 2003-02-07 papers/hypertext2003/paper.tex
Added paragraph about dev cycle.

@@
 
-\title{\tw:  Building a Xanalogical System in Nine Days}
+\title{\tw:  Building a Xanalogical System in Ten Days}
 
@@
 
-Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \ was implented from scratch in nine days by one person.  
+Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \ was implented from scratch in ten days by one person.  
 We attribute this success to the maturity of modern technology and design techniques.  
@@
 \section{System Architecture}
-We designed and built \tw, a full-featured xanalogical system, from scratch in only nine days.
+We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days.
 To acheive this kind of rapid development, we relied heavily on modern technology and design techniques.
@@
 Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
-For example, highlighting possible misspellings in preview mode was a minor addition that required less than ten lines of code.
+For example, highlighting possible misspellings in preview mode was a minor addition that required less than fifteen lines of code.
 
@@
 Other systems that have used this development method successfully are discussed in Section \ref{sec:RelatedWork}.
+
+Even though the full development cycle was short, we used an iterative process.
+Features were added one at a time to the system, and the system was maintained in a usable form at all times.
+For example, we started with a system that managed text chunks, then added document management, then added quotes, then added tokens transfers, {\it etc.}
+Final iterations added features such as spell checking and index-based searching.
+From our understanding of previous xanalogical implementation efforts, this iterative process may have been key to our success.
+The Xanadu model is complex and subtle, and it is easy to get bogged down by details without ever producing a working system.
+Our system started out simple and grew in complexity, feature by feature.
 

### 2003-02-11 tokenWord.pl
Added support for backup/restore of data directory as a tarball.

@@ -62,6 +62,9 @@
 # Set up a local error log.  Changed to work with apnrecords.org server.
 # Changed to log user in immediately after account creation.
 #
+# 2003-February-11   Jason Rohrer
+# Added support for backup/restore of data directory as a tarball.
+#
 
 
 
@@ -117,6 +120,7 @@ $cgiQuery->cache( 1 );
 
 
 my $action = $cgiQuery->param( "action" ) || '';
+
 
 
 # get the cookie, if it exists
@@ -224,6 +228,83 @@ if( $payerEmail ne "" and $paymentGross ne "" and $paypalCustom ne "" ) {
                        "$paymentDate  $user  ".
                        "$payerEmail  $paymentGross  $numTokens\n" );
         }            
+    }
+}
+elsif( $action eq "getDataTarball" ) {
+    my $password = $cgiQuery->param( "password" ) || '';
+    
+    my $truePassword = readFileValue( "$dataDirectory/admin.pass" );
+
+    if( $password eq $truePassword ) {
+    
+        print $cgiQuery->header( -type=>'application-x/gzip', -expires=>'now',
+                                 -Cache_control=>'no-cache' );
+        my $oldPath = $ENV{ "PATH" };
+        $ENV{ "PATH" } = "";
+
+        open( TARBALL_READER, 
+  "cd $dataDirectory/..; /bin/tar cf - $dataDirectoryName | /bin/gzip -f |" );
+        while( <TARBALL_READER> ) {
+            print "$_";
+        }
+        close( TARBALL_READER );
+
+        $ENV{ "PATH" } = $oldPath;
+    }
+    else {
+        print $cgiQuery->header( -type=>'text/html', -expires=>'now',
+                                 -Cache_control=>'no-cache' );
+        print "access denied";
+    }
+}
+elsif( $action eq "makeDataTarball" ) {
+    my $password = $cgiQuery->param( "password" ) || '';
+    
+    my $truePassword = readFileValue( "$dataDirectory/admin.pass" );
+
+    if( $password eq $truePassword ) {
+    
+        print $cgiQuery->header( -type=>'text/html', -expires=>'now',
+                                 -Cache_control=>'no-cache' );
+        my $oldPath = $ENV{ "PATH" };
+        $ENV{ "PATH" } = "";
+
+        my $outcome =
[…]

### 2003-02-11 tokenWord.pl
Added creation of accounting directory.

@@ -1,4 +1,4 @@
-#!/usr//bin/perl -wT
+#!/usr/bin/perl -wT
 
 # for apnrecords.org server
 #!/usr/local/bin/perl -wT
@@ -64,6 +64,7 @@
 #
 # 2003-February-11   Jason Rohrer
 # Added support for backup/restore of data directory as a tarball.
+# Added creation of accounting directory.
 #
 
 
@@ -1136,6 +1137,7 @@ sub setupDataDirectory {
 
         mkdir( "$dataDirectory/index", oct( "0777" ) );
         mkdir( "$dataDirectory/temp", oct( "0777" ) );
+        mkdir( "$dataDirectory/accounting", oct( "0777" ) );
 
         writeFile( "$dataDirectory/topDocuments/mostQuoted", "" );
         writeFile( "$dataDirectory/topDocuments/mostRecent", "" );

### 2003-02-12 papers/hypertext2003/paper.tex
Fixed wording, and fixed a reference.
Added a reference chain diagram.

@@
 \documentclass{acm_proc_article-sp}
+\usepackage{graphs}
 
@@
 
+\subsubsection{Data Model}
 Keeping with the Xanadu model, \tw \ separates documents from the text they contain.
@@
 Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.
+
+Each reference in a document contains a pointer to text chunk region and an optional pointer to a document context region.
+The document context pointer tracks which document the material was quoted from and is used for quote reference chasing.
+If a document refers to a new text chunk that has not appeared in any previous documents, the document context pointer is omitted:  such chunks are not part of quotes and have no references that can be chased.
+With this two-pointer model, we can distinguish ``original'' material in a document from quoted material and support recursive reference chasing.
+When following a quote reference, a chain of referneces may need to be chased before the original context of the text is found.
+
+For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote original material, residing in chunk $k$, from document $C$.  
+$A$'s reference will contain both a pointer to the text chunk $k$ and to the document context $B$.  
+$B$'s reference will point to both chunk $k$ and document $C$.  
+At the end of this reference chain, $C$'s reference will point only to $k$.
+
+\begin{figure*}[t]
+\begin{center}
+
+\begin{graph}(8,4)(-4,-1.65)
+\graphnodesize{0.6}
+\graphnodecolour{1}
+\opaquetextfalse
+
+\rectnode{A}[1.5,2](-6,0)[\fillednodesfalse]     
+\autonodetext{A}[n]{Document $A$}
+\roundnode{kInAAnchor}(-5.45,.25)[\graphnodecolour{0}\graphnodesize{0.1}]
+\rectnode{AQuote}[1.5,0.75](-6,.25)[\graphnodecolour{0.5}]  
+\rectnode{kInA}[1.5,0.5](-6,.25)[\graphnodecolour{0.85}]
+
+\rectnode{B}[1.5,2](-2,0)[\fillednodesfalse]
+\autonodetext{B}[s]{Document $B$}
+\roundnode{kInBAnchor}(-1.45,-.5)[\graphnodecolour{0}\graphnodesize{0.1}]
+\rectnode{AQuoteInB}[1.5,0.75](-2,-.5)[\graphnodecolour{0.5}]
+\rectnode{BQuote}[1.5,0.5](-2,-.5)[\graphnodecolour{0.85}]
+
+\rectnode{C}[1.5,2](2,0)[\fillednodesfalse]      
+\autonodetext{C}[n]{Document $C$}
+\rectnode{kInC}[1.5,1](2,0)[\graphnodecolour{.85}]
+\rectnode{BQuoteInC}[1.5,0.5](2,.125)[\graphnodecolour{0.85}]
+
+\rectnode{k}[1.5,1](6,0)[\graphnodecolour{.85}]      
+\autonodetext{k}[n]{Chunk $k$}
+
+\diredge{AQuote}{AQuoteInB}[\graphlinedash{4 4}\grapharrowtype{2}]
+\dirbow{kInAAnchor}{k}{0.17}[\grapharrowtype{1}]
+
+\diredge{BQuote}{BQuoteInC}[\graphlinedash{4 4}\grapharrowtype{2}]
+\dirbow{kInBAnchor}{k}{-0.17}[\grapharrowtype{1}]
+
+\diredge{kInC}{k}[\grapharrowtype{1}]
+
+\end{graph}
+
+\caption{An example reference chain.
+Dotted arrows represent document pointers, and solid arrows represent chunk pointers.
+Light gray regions represent text from chunk $k$.
+Dark gray regions in $A$ and $B$ represent portions of $A$'s quote from $B$ that do not come from chunk $k$ (other chunks are omitted from this diagram for clarity).}
+\label{fig:referenceChain}
+
+\end{center}
+
+\end{figure*}
+
 Quote clipboards, like documents, contain a list of references.
@@
 The chunks associated with a quote are only resolved when the quote is used as part of a new document.
-
-\subsubsection{Development}
-The entire \tw \  system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
-Perl's built-in support for regular expressions was very useful for the rather complicated text processing done by \tw.
-Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
-For example, highlighting possible misspellings in preview mode was a minor addition that required less than fifteen lines of code.
-
-CGI programming is well-supported in Perl, and HTML made user interface layout and user action processing easy to implement.
-Perl-based CGI programming seems to be the modern method of choice for rapidly developing complex, multi-user applications.
-Other systems that have used this development method successfully are discussed in Section \ref{sec:RelatedWork}.
-
-Even though the full development cycle was short, we used an iterative process.
-Features were added one at a time to the system, and the system was maintained in a usable form at all times.
-For example, we started with a system that managed text chunks, then added document management, then added quotes, then added tokens transfers, {\it etc.}
-Final iterations added features such as spell checking and index-based searching.
-From our understanding of previous xanalogical implementation efforts, this iterative process may have been key to our success.
-The Xanadu model is complex and subtle, and it is easy to get bogged down by details without ever producing a working system.
-Our system started out simple and grew in complexity, feature by feature.
 
@@
 When a document is added to the system, it is appended to the end of the index list for each word that it contains.
+
+\subsubsection{Development}
+The entire \tw \  system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
+Perl's built-in support for regular expressions was very useful for the rather complicated text processing done by \tw.
+Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
+For example, highlighting possible misspellings in preview mode was a minor addition that required less than fifteen lines of code.
+
+CGI programming is well-supported in Perl, and HTML made user interface layout and user action processing easy to implement.
+Perl-based CGI programming seems to be the modern method of choice for rapidly developing complex, multi-user applications.
+Other systems that have used this development method successfully are discussed in Section \ref{sec:RelatedWork}.
+
+Even though the full development cycle was short, we used an iterative process.
+Features were added one at a time to the system, and the system was maintained in a usable form at all times.
+For example, we started with a system that managed text chunks, then added document management, then added quotes, then added tokens transfers, {\it etc.}
+Final iterations added features such as spell checking and index-based searching.
+From our understanding of previous xanalogical implementation efforts, this iterative process may have been key to our success.
+The Xanadu model is complex and subtle, and it is easy to get bogged down by details without ever producing a working system.
+Our system started out simple and grew in complexity, feature by feature.
 
@@
 ``Xanadu'' is a trademark of Ted Nelson.
-To prevent confusion, the generic terms ({\it e.g.}, xanalogical) have been used wherever possible.
+To prevent confusion, the generic terms ({\it e.g.}, xanalogical system) have been used wherever possible.
 

### 2003-02-12 papers/hypertext2003/paper.tex
Added double arrorws to represent regions.
Added a quote clipboard model diagram.

@@
 At the end of this reference chain, $C$'s reference will point only to $k$.
+Figure \ref{fig:referenceChain} shows a diagram of this reference chain.
 
@@
 \rectnode{A}[1.5,2](-6,0)[\fillednodesfalse]     
-\autonodetext{A}[n]{Document $A$}
-\roundnode{kInAAnchor}(-5.45,.25)[\graphnodecolour{0}\graphnodesize{0.1}]
+\nodetext{A}(0,1.25){Document $A$}
 \rectnode{AQuote}[1.5,0.75](-6,.25)[\graphnodecolour{0.5}]  
 \rectnode{kInA}[1.5,0.5](-6,.25)[\graphnodecolour{0.85}]
+\roundnode{kInAStartAnchor}(-5.25,.5)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{kInAEndAnchor}(-5.25,0)[\graphnodecolour{0}\graphnodesize{0}]
+
+\roundnode{QuoteInAStartAnchor}(-5.25,.625)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{QuoteInAEndAnchor}(-5.25,-.125)[\graphnodecolour{0}\graphnodesize{0}]
 
 \rectnode{B}[1.5,2](-2,0)[\fillednodesfalse]
-\autonodetext{B}[s]{Document $B$}
+\nodetext{B}(0,-1.25){Document $B$}
 \roundnode{kInBAnchor}(-1.45,-.5)[\graphnodecolour{0}\graphnodesize{0.1}]
@@
 
+\roundnode{AQuoteInBStartAnchor}(-2.75,-.125)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{AQuoteInBEndAnchor}(-2.75,-.875)[\graphnodecolour{0}\graphnodesize{0}]
+
+\roundnode{QuoteInBStartAnchor}(-1.25,-.25)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{QuoteInBEndAnchor}(-1.25,-.75)[\graphnodecolour{0}\graphnodesize{0}]
+
 \rectnode{C}[1.5,2](2,0)[\fillednodesfalse]      
-\autonodetext{C}[n]{Document $C$}
+\nodetext{C}(-.75,1.25){Document $C$}
 \rectnode{kInC}[1.5,1](2,0)[\graphnodecolour{.85}]
@@
 
+\roundnode{BQuoteInCStartAnchor}(1.25,.375)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{BQuoteInCEndAnchor}(1.25,-.125)[\graphnodecolour{0}\graphnodesize{0}]
+
+\roundnode{kInCStartAnchor}(2.75,.5)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{kInCEndAnchor}(2.75,-.5)[\graphnodecolour{0}\graphnodesize{0}]
+
 \rectnode{k}[1.5,1](6,0)[\graphnodecolour{.85}]      
 \autonodetext{k}[n]{Chunk $k$}
+\rectnode{QuoteInK}[1.5,0.5](6,.125)[\graphnodecolour{0.85}]
+\roundnode{QuoteInKStartAnchor}(5.25,.375)[\graphnodesize{0}\graphnodecolour{0}]
+\roundnode{QuoteInKEndAnchor}(5.25,-.125)[\graphnodesize{0}\graphnodecolour{0}]
 
-\diredge{AQuote}{AQuoteInB}[\graphlinedash{4 4}\grapharrowtype{2}]
-\dirbow{kInAAnchor}{k}{0.17}[\grapharrowtype{1}]
+\roundnode{kStartAnchor}(5.25,.5)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{kEndAnchor}(5.25,-.5)[\graphnodecolour{0}\graphnodesize{0}]
 
-\diredge{BQuote}{BQuoteInC}[\graphlinedash{4 4}\grapharrowtype{2}]
-\dirbow{kInBAnchor}{k}{-0.17}[\grapharrowtype{1}]
+\diredge{QuoteInAStartAnchor}{AQuoteInBStartAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+\diredge{QuoteInAEndAnchor}{AQuoteInBEndAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+\dirbow{kInAStartAnchor}{QuoteInKStartAnchor}{0.17}[\grapharrowtype{1}]
+\dirbow{kInAEndAnchor}{QuoteInKEndAnchor}{0.17}[\grapharrowtype{1}]
 
-\diredge{kInC}{k}[\grapharrowtype{1}]
+\diredge{QuoteInBStartAnchor}{BQuoteInCStartAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+\diredge{QuoteInBEndAnchor}{BQuoteInCEndAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+
+\dirbow{QuoteInBStartAnchor}{QuoteInKStartAnchor}{-0.19}[\grapharrowtype{1}]
+\dirbow{QuoteInBEndAnchor}{QuoteInKEndAnchor}{-0.19}[\grapharrowtype{1}]
+
+\dirbow{kInCStartAnchor}{kStartAnchor}{.17}[\grapharrowtype{1}]
+\dirbow{kInCEndAnchor}{kEndAnchor}{.17}[\grapharrowtype{1}]
 
@@
 \caption{An example reference chain.
-Dotted arrows represent document pointers, and solid arrows represent chunk pointers.
+Dotted lines represent document region pointers, and solid arcs represent chunk region pointers.
 Light gray regions represent text from chunk $k$.
@@
 
-Quote clipboards, like documents, contain a list of references.
-However, to support showing the context of a quote, the references are not to chunks, but to the context documents themselves.
-The chunks associated with a quote are only resolved when the quote is used as part of a new document.
+Quote clipboards are modeled in the following way.
+Each quote on the clipboard points to a contiguous document region.
+Since a  document region can be comprised of regions from multiple chunks, we might want to model each quote as a list of references, just like we model a document.
+However, we simplify the clipboard by modeling each quote as a single document region pointer with no chunk region pointers.
+To insert a clipboard quote into a new document, we can resolve the chunk region references for the quote and set the document region for each of these references to the document from which the quote was extracted.
+This model allows us both to track the extraction context of the quote and to store the quote clipboard efficiently.
+Figure \ref{fig:quoteClipboardModel} shows a diagram of a quote clipboard modeled in this way.
+The alternative list model mentioned above could not be easily used to track quote extraction context, and the clipboard representation would be much larger.
+
+\begin{figure}[b]
+\begin{center}
+
+\begin{graph}(6.5,2.5)(-3.25,-1.25)
+\graphnodesize{0.6}
+\graphnodecolour{1}
+\opaquetextfalse
+
+\rectnode{q0}[1.0,0.5](0,0)
+\nodetext{q0}{$q0$}
+\autonodetext{q0}[n]{Clipboard}
+\roundnode{q0Anchor}(.5,0)[\graphnodecolour{0}\graphnodesize{0}]
+\rectnode{q1}[1.0,0.5](0,-.5)
+\nodetext{q1}{$q1$}
+\roundnode{q1Anchor}(-.5,-.5)[\graphnodecolour{0}\graphnodesize{0}]
+
+\rectnode{A}[1.5,2](2.5,0)     
+\autonodetext{A}[n]{Document $A$}
+\rectnode{AQuote}[1.5,0.75](2.5,.25)  
+\roundnode{QuoteInAStartAnchor}(1.75,.625)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{QuoteInAEndAnchor}(1.75,-.125)[\graphnodecolour{0}\graphnodesize{0}]
+
+\rectnode{B}[1.5,2](-2.5,0)     
+\autonodetext{B}[n]{Document $B$}
+\rectnode{BQuote}[1.5,0.5](-2.5,-.25)  
+\roundnode{QuoteInBStartAnchor}(-1.75,0)[\graphnodecolour{0}\graphnodesize{0}]
+\roundnode{QuoteInBEndAnchor}(-1.75,-.5)[\graphnodecolour{0}\graphnodesize{0}]
+
+\diredge{q0Anchor}{QuoteInAStartAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+\diredge{q0Anchor}{QuoteInAEndAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+
+\diredge{q1Anchor}{QuoteInBStartAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+\diredge{q1Anchor}{QuoteInBEndAnchor}[\graphlinedash{4 4}\grapharrowtype{2}]
+
+\end{graph}
+
+\caption{An example quote clipboard.  Dotted lines represent document region pointers.}
+\label{fig:quoteClipboardModel}
+
+\end{center}
+
+\end{figure}
 

### 2003-02-12 papers/hypertext2003/paper.tex
Added more example representation strings, and fixed some layout issues.

@@
 With this two-pointer model, we can distinguish ``original'' material in a document from quoted material and support recursive reference chasing.
-When following a quote reference, a chain of referneces may need to be chased before the original context of the text is found.
+By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
+%When following a quote reference, a chain of referneces may need to be chased before the original context of the text is found.
 
@@
 
-\caption{An example reference chain.
+\caption{An example reference chain model.
 Dotted lines represent document region pointers, and solid arcs represent chunk region pointers.
@@
 
-\begin{graph}(6.5,2.5)(-3.25,-1.25)
+\begin{graph}(6.5,2.8)(-3.25,-1.0)
 \graphnodesize{0.6}
@@
 
-\caption{An example quote clipboard.  Dotted lines represent document region pointers.}
+\caption{An example quote clipboard model.  Dotted lines represent document region pointers.}
 \label{fig:quoteClipboardModel}
@@
 \subsubsection{Data Representation}
-The system data is stored in a directory tree on the filesystem.
-Each user has directory that stores that user's chunk files, document files, and quote clipboard files, along with a list of previously purchased chunk regions.
+The system data is stored in a filesystem directory tree.
+Each user has directory that holds that user's chunk files, document files, and quote clipboard files, along with a list of previously purchased chunk regions.
 To support two-way reference chasing, each document has a file that tracks the documents that quote it.
 
-References throughout the system are stored in the following form:
+References in documents are represented using the following format:
 \begin{center}
@@
 \end{center}
-The portion of the reference befor the ``;'' describes the text chunk of the reference.  
-The second portion, which is optional, describes the quote context of the reference.  
+The portion of the reference before the ``;'' describes the chunk region of the reference.  
+The second portion, which is optional, describes the document region context of the reference.  
 Note that {\tt chunkUserID} may differ from {\tt docUserID}, since the quote context may be part of a quote in another document.
-For example, document $A$ may quote from document $B$, but the portion that $A$ quotes may be part of $B$'s quote from document $C$.
-In this example, the reference included in $A$ might look like this:
+Consider our previous example, which is shown in Figure \ref{fig:referenceChain}, and suppose that documents $B$ and  $C$ are owned by {\tt userY} and {\tt userZ}, respectively.
+%For example, document $A$ may quote from document $B$, but the portion that $A$ quotes may be part of $B$'s quote from document $C$.
+The reference included in document $A$ might look like this:
 \begin{center}
-{\tt <userC, C, 105, 38; userB, B, 421>} 
+{\tt <userX, k, 12, 50; userY, B, 125>} 
 \end{center}
-Note that {\tt length} is not specified for the document context of a reference, since it would be redundant.
+In other words, we have 50 characters from chunk $k$, starting with character 13, which were quoted from document $B$, starting at character 126.
+Note that {\tt length} is not specified for the document region context of a reference, since it would be redundant (in our example, it would be 50).
 
-With this representation, a reference can be used both to fetch the required text chunk region and to display context in case of a followed quote reference.
-By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
-When a new chunk is created as part of a document, the context portion of the reference is ommited, indicating that the document is the first context in which this chunk was used.
+%With this representation, a reference can be used both to fetch the required text chunk region and to display context in case of a followed quote reference.
+%By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
+%When a new chunk is created as part of a document, the context portion of the reference is ommited, indicating that the document is the first context in which this chunk was used.
+
+As described in our discussion of data models, each quote on a clipboard has only a single pointer to a document region and no chunk region pointers.
+We represent these references with the following format:
+\begin{center}
+{\tt <docUserID, docID, startOffset, length>} 
+\end{center}
+Consider our previous example clipboard, which is shown in Figure \ref{fig:quoteClipboardModel}, and suppose that documents $A$ and  $B$ are owned by {\tt userX} and {\tt userY}, respectively.
+The clipboard representation might look like this:
+\begin{center}
+{\tt <userX, A, 37, 75>}\\
+{\tt <userY, B, 100, 50>}\\ 
+\end{center}
 

### 2003-02-12 papers/hypertext2003/paper.tex
Added a section on scalability limitations, and added a reference.

@@
 The second portion, which is optional, describes the document region context of the reference.  
-Note that {\tt chunkUserID} may differ from {\tt docUserID}, since the quote context may be part of a quote in another document.
+Note that {\tt chunkUserID} may differ from {\tt docUserID}, since the quoted region may itself be part of a quote in the context document (in the case of a nested quote).
 Consider our previous example, which is shown in Figure \ref{fig:referenceChain}, and suppose that documents $B$ and  $C$ are owned by {\tt userY} and {\tt userZ}, respectively.
@@
 \begin{center}
-{\tt <userX, k, 12, 50; userY, B, 125>} 
+{\tt <userZ, k, 12, 50; userY, B, 125>} 
 \end{center}
 In other words, we have 50 characters from chunk $k$, starting with character 13, which were quoted from document $B$, starting at character 126.
+{\tt userZ} owns both document $C$ and chunk $k$, since $k$ was created as original material for use in $C$.
 Note that {\tt length} is not specified for the document region context of a reference, since it would be redundant (in our example, it would be 50).
@@
 Each word in the index is associated with a list of documents containing that word.
-When a document is added to the system, it is appended to the end of the index list for each word that it contains.
+When a document is added to the system, its reference is appended to the end of the index list for each word that it contains.
 
@@
 
-\subsubsection{Implementation Limitations}
-The main limitation of our implementation is the use of a filesystem as a data backend.
+\subsubsection{Scalability Limitations}
+The main scalability limitation of our implementation is the use of a filesystem as a data backend.
+Each text chunk and document are stored in a separate file, and these data objects can be quite small.
+A chunk file will be as large as the text it contains, but a document file stores only references.
+For example, if a new document is created that references only one new chunk and contains no quotes, the document file will contain a single reference.
+The example reference given above was represented using only 33 bytes of ASCII text.
+
+The first limitation is in terms of storage efficiency:  most filesystems have a minimum file size, and this minimum is usually larger than 1 kilobyte.
+In our example, 33 bytes of data would occupy at least a kilobyte of disk space.
+
+The second limitation is in terms of filesystem architecture:  Unix-like filesystems use an inode table, and each file must be associated with an inode.
+When a filesystem is created, the number of available inodes is fixed, and this number can be relatively small (the common ratio for modern Linux systems seems to be about 200,000 inodes per gigabyte of disk space).
+\cite{OperatingSystems}
+Ignoring storage efficiency concerns, our implementation is limited in terms of the number of chunks and documents it can contain.
+
+If our system did need to scale to support millions of users and billions of chunks and documents, several approaches would be possible.
+First, we could use an existing database system as a backend to store chunks and documents.
+This approach would deal with the inode limitations, and it might actually improve performance, since database queries would replace the directory lookups that are currently used to fetch chunks and documents.
+A second approach would be to implement a simple application-level virtual filesystem for chunk and document storage.
+With this approach, we could taylor the storage system to our specific needs, though it would certainly be labor-intensive.
+
+All filesystem operations in \tw \ are wrapped by a single module with only a handful of interface functions.
+By modifying the implementation of these module functions, either of the scalable backends mentioned above could be added to \tw \ with no changes to the rest of the code.
+
+We chose a filesystem backend, despite its scalability limitations, because of its simplicity.
+This choice fits into our implementation philosophy, since the focus was on producing a working system and adding features iteratively.
+A scalable backend might be seen as a feature to be added in a future iteration.
+Our system, in its current form, is still functional in terms of its goals:  it could support hundreds of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
 

### 2003-02-13 papers/hypertext2003/paper.tex
Added section on micropayments.

@@
 \section{Introduction}
+\label{sec:Introduction}
 Xanadu has been floating in the collective mind of the hypertext research community for nearly forty years.
@@
 
+\label{sec:Xanadu}
 As mentioned in the above quote, Xanadu's underlying ideas were first incubated by Nelson in the 1960s \cite{Nelson1965}.  
@@
 The entire \tw \  system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
-Perl's built-in support for regular expressions was very useful for the rather complicated text processing done by \tw.
-Many of these text processing operations could be expressed in succinct and elegant ways using Perl.
+Perl's built-in support for regular expressions was useful for the rather complicated text processing done by \tw.
+Many of these text processing operations can be expressed in succinct and elegant ways using Perl.
 For example, highlighting possible misspellings in preview mode was a minor addition that required less than fifteen lines of code.
 
-CGI programming is well-supported in Perl, and HTML made user interface layout and user action processing easy to implement.
+User interfaces can be layed out easily with HTML, and CGI processing is well-supported by existing Perl modules.
+The CGI model requires a stateless action-response programming style, which makes it easy to focus on one feature at a time during development.
 Perl-based CGI programming seems to be the modern method of choice for rapidly developing complex, multi-user applications.
@@
 
-\subsection{Xanalogical Improvements}
+%\subsection{Xanalogical Improvements}
 
-\subsection{Missing Features}
+%\subsection{Missing Features}
 
 \section{Micropayment Issues}
+With our micropyament system, we wanted to leverage PayPal's \cite{paypal} immense popularity and familiarity.
+By handling real-world currency exclusively through PayPal, instead of through our own virtual money system, we can process payments in a secure and trustworthy fashion.
+
+However, PayPal's currency model does not support the microdollar resolution that we need, so we cannot rely on this service alone for transfering tokens between users.
+Even if PayPal did support high-resolution payments, it does not allow a third party to initiate transfers between account holders in a transparent and frictionless way (and for good reason, given the security issues).
+
+To deal with these issues, we built an internal token balance system and used PayPal integration only for deposits and withdrawls of real-world currency.
+For example, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tw \ documents.
+Similarly, withdrawing tokens in exchange for real-world currency is not frictionless: 
+PayPal does not support an automated payment mechanism, so withdrawl requests are queued for manual processing by the \tw \ system administrator.
+Whereas deposits take effect immediately (using PayPal's ``Instant Payment Notification'' service), withdrawn token refunds are delayed by the response of the human administrator.
+From the administrator's point of view, the withdrawl queue can be used to increase security, since any suspicious activity can be investigated before real-world payments are made.
 
 \subsection{Balancing Risk}
+Given that micropayments in \tw \ are mandatory and automatic, a major barrier to system adoption might exist:  trying \tw \ would require the deposit of real-world currency.
+Even the main page displayed after login is a first-class \tw \ document, so a new user with no tokens would not be able to read a description of \tw, let alone try any of its features.
+
+One way of dealing with this adoption barrier would be to give each new user a small number of ``free'' tokens to start with (for example, at least enough tokens to read the main page).
+This solution would allow new users to try the system with no monetary investment, but it carries an enormous risk for the \tw \ system administrators.
+A small group of users could create many fake accounts and then use each account to read a large dummy document owned by one user.
+This kind of scam could be used to consolodate the free starting tokens from many accounts into one account, and then a withdrawl could be made in exchange for a large amount of real-world currency.
+Even if users are not trying to intentially scam the system, doling out free tokens poses considerable risk.
+One user might write documents that are popular with new users (for example, a collection of how-to documents) and ammass a large number of free tokens over time---the withdrawl of these tokens could financially devastate the \tw \ administrators.
+
+We have devised a risk-free mechanism that deals with the adoption barrier.  
+Our approach uses two token types.
+The first type of tokens, called {\it trial} tokens, have no real-world value.
+Each new account starts out with a small number of trial tokens (in our live system, each account starts with 50,000 trial tokens).
+The second type of tokens, called {\it real} tokens, can be exchanged for real-world currency.
+Token transfers inside \tw \ keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
+Trial tokens are favored, and real tokens are only spent when a user has no trial tokens.
+
+For example, suppose the balances of three users are as shown in following table:
+%suppose user $A$ has a trial:real token balance of 50:200, user $B$ has a balance of 0:500, and user $C$ has a balance of 10:0.
+\begin{center}
+\begin{tabular}{|l||r|r|}
+\hline
+User&Trial balance &Real balance\\
+\hline
+$A$&50 &200\\
+\hline
+$B$&0  &500\\
+\hline
+$C$&10 &0  \\
+\hline
+\end{tabular}
+\end{center}
+Suppose that user $A$ reads a new 100-chracter document that is owned by $B$, but that the document contains a 20-character quote by $C$.
+The resulting balances are shown in the following table:
+\begin{center}
+\begin{tabular}{|l||r|r|}
+\hline
+User&Trial balance &Real balance\\
+\hline
+$A$&0 &150\\
+\hline
+$B$&50  &520\\
+\hline
+$C$&10 &20  \\
+\hline
+\end{tabular}
+\end{center}
+
+%$A$'s new balance would be 0:150, $B$'s new balance would be 50:520, and $C$'s new balance would be 10:20.
+
+This two-type scheme allows users to try \tw \ extensively without a monetary investment, and it also poses no financial risks to the administrators.
+Note that though trial tokens have no real-world value, they still have value inside \tw, since they can always be used to purchase new content.
+Inside \tw, a user that amasses many trial tokens is just as wealthy as a user with many real tokens.
+A user that actively published popular content in \tw \ could effectively use the system forever without depositing any real-world money.
 
@@
 \label{sec:RelatedWork}
+
+Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}.
 

### 2003-02-13 papers/hypertext2003/paper.tex
Added a related work section, and another reference.

@@
 
-Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}.
+Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}, so we will focus on related non-xanalogical systems here.
+However, we should mention that interest in xanalogical systems has not waned in recent years.
+For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
 
-Wikis
-\cite{WikiWikiWeb}
-\cite{Wikipedia}
+\subsection{Wikis}
 
-Everything2
-\cite{Everything2}
+In terms of implementation, \tw \ is closely related to a recent class of hypertext systems known as Wikis, which are often implemented as Perl-based CGI programs.
+Wikis are reader-edited web sites, and web-based HTML forms are used as the interface for page authoring.
+In many cases, Wikis are open for editing by the public at large.
 
-Weblogs
-\cite{kuro5hin}
+Aside from the sociological issues, Wikis approach hypertext in an interesting way.
+Links can be created in a document to documents that do not exist without knowing where those documents will eventually reside.
+To create a new document, a user must follow one of these dangling links in an existing page, which leads to a page creation screen.
+Thus, in a Wiki, there is no way to create a page in isolation.
+In fact, the name of a new page is determined by the contents of the dangling link and cannot be specified in the page creation screen.
 
-Xanadu
+\tw \ differs from a Wiki in its approach to hypertext, since a \tw \ quote can only be taken from an existing document.
+No mechanism is provided for refering to a document that does not yet exist.
+
+The first Wiki was created by Ward Cunningham in 1995 and is still active today\cite{WikiWikiWeb}.
+The most ambitious Wiki-based project is Wikipedia, a user-edited encyclopedia, which recently grew to over 100,000 entries \cite{Wikipedia}.
+
+\subsection{Everything2}
+Like \tw \ and Wikis, Everything2 is a web-based hypertext system implemented using CGI and Perl \cite{Everything2}.
+Everything2 supports dangling links to pages that do not exist yet, but it handles these links differently than a Wiki does.
+When a user follows a dangling link, a search is performed for the title of the non-existant page.
+Thus, dangling links are fuctional from a reader's point of view.
+We might conclude that Wikis favor authors, while Everything2 favors readers.
+As soon as a page is created that matches the title of a dangling link, that link points to the new page directly.
+
+In addition to in-line, user-created links (dangling or otherwise), each node in Everything2 features a list of automatically generated links.
+These links are culled from user traversal paths:  when a user leaves one page and enters another (either by clicking a link or performing a search), a two-way link is added between the pages.
+
+\subsection{Weblogs}
+Another class of related web based hypertext systems are weblogs, or ``blogs.''
+These systems allow content to be added to a web site serially, one post at a time.
+Some blogs are used by individuals as a means of sharing daily thoughts with the world, while others aim to be collaborative information spaces filled with moderated comments posted by the public.
+One of the most interesting collaborative weblogs is Kuro5hin (pronounced ``corrosion''), which features high-quality news and culture stories submitted and moderated by the public \cite{kuro5hin}.
+Many blogs are implemented using CGI and Perl, though more recent efforts seem to favor PHP.
+
+\subsection{Commonalities and Differences}
+All three systems share several aspects in common with \tw.
+First, they are all web-based, collaborative information spaces.
+Second, they all relie heavily on existing technology for their implementations.
+Third, from what we can tell, they were developed relatively quickly.
+
+In addition, we can see iterative development philosophies in weblogs and Wikis, not necessarily in the individual projects, but in the phenomena themselves.
+The first Wikis and weblogs were simple but functional.
+Over time, new implementations were released with more features.
+Today, the most popular systems in either category are extraordinarily feature-rich.
+
+Of course, out of all of the collaborative information spaces discussed here, \tw \ is the only system that supports deep content reuse and frictionless micropayments.
+Thus, these systems are closely related in terms of implementation, but their goals are very different.
 

### 2003-02-13 papers/hypertext2003/paper.tex
Finished writing of paper body.

@@
 \begin{abstract}
-We describe \tw, a web-based xanalogical hypertext system.  Our system supports almost every feature associated with Xanadu, an architecture that has been actively discussed for nearly forty years.
+We describe \tw, a web-based xanalogical hypertext system.
+Our system supports almost every core feature associated with Xanadu, an architecture that has been actively discussed for nearly forty years.
 Features include deep quotation, unbreakable references, two-way reference chasing, and frictionless micropayments that are backed by real-world currency.
@@
 Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \ was implented from scratch in ten days by one person.  
-We attribute this success to the maturity of modern technology and design techniques.  
-In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
+We attribute this success to the maturity of modern technology and development techniques.  
+%In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
 A live \tw \ system is running at:
@@
 \cite{OperatingSystems}
-Ignoring storage efficiency concerns, our implementation is limited in terms of the number of chunks and documents it can contain.
+Thus, even if we ignore storage efficiency concerns, our implementation is limited in terms of the number of chunks and documents it can contain.
 
@@
 A scalable backend might be seen as a feature to be added in a future iteration.
-Our system, in its current form, is still functional in terms of its goals:  it could support hundreds of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
+Our system, in its current form, is still functional in terms of its goals:  it can potentially support hundreds of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
 
@@
 To deal with these issues, we built an internal token balance system and used PayPal integration only for deposits and withdrawls of real-world currency.
-For example, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tw \ documents.
+With this configuration, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tw \ documents.
 Similarly, withdrawing tokens in exchange for real-world currency is not frictionless: 
@@
 \subsection{Commonalities and Differences}
-All three systems share several aspects in common with \tw.
+All three systems discussed above share several features in common with \tw.
 First, they are all web-based, collaborative information spaces.
-Second, they all relie heavily on existing technology for their implementations.
+Second, they all rely heavily on existing technology for their implementations.
 Third, from what we can tell, they were developed relatively quickly.
@@
 Of course, out of all of the collaborative information spaces discussed here, \tw \ is the only system that supports deep content reuse and frictionless micropayments.
-Thus, these systems are closely related in terms of implementation, but their goals are very different.
+Thus, these systems are closely related in terms of implementation, but their goals and end-user experiences are very different.
 
 \section{Conclusion}
+Thoughout this paper, we have discussed the strategies that made \tw \ development possible, including an interative process and heavy use of existing technology.
+
+One additional strategy was crucial, though it has not been mention explicitly:  a focus on a core xanalogical feature set.
+We set out to build a system that supported deep quotation, unbreakable references, and frictionless micropayments.
+In Section \ref{sec:Xanadu}, we distilled these features from the Xanadu model.
+However, {\it Literary Machines} is over 250 pages long, and it is choked full of features that an ideal xanalogical system might have \cite{NelsonLiteraryMachines}.
+Perhaps previous Xanadu efforts aimed for this ideal feature set, and perhaps this is why they failed.
+
+\tw \ is by no means the ideal xanalogical system, and many features are missing.
+However, it is still the first system to implement the core features of the Xanadu architecture.
+Though one would be hard-pressed to argue that the features included in \tw \ are not crucial, three important features are missing.
+First, \tw \ does not explicitly support document versioning.
+However, using the quotation primitive, a limited form of versioning can be emulated (a user can quote unchanged regions of the previous version when creating a new version).
+Second, \tw \ does not support multi-server integration:  each installation of \tw \ operates in isolation, and quotes between documents at different sites are not possible.
+We see multi-server integration as one of the weakpoints in the Xanadu model:  how can we ensure that references never break in a system comprised of multiple, separately owned servers?
+Even if fault-tolerant, multi-server integration is possible, it is not essential for the end-user experience. 
+Third, \tw \  does not support the side-by-side document comparission with {\it transpointing} lines, a classic Xanadu feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
+The transpointing interface would be difficult, if not impossible, to support in a web browser with no additional software.
+However, a side-by-side document comparisson interface, using colored highlighting to indicate itentical regions, has been contemplated for \tw.
+Implementing such an interface would be easy, though coming up with a highlighting scheme that works correctly in the general case (for example, without running out of readable colors) is quite difficult.
+
+In recent personal conversations, Nelson has described a layered presentation model that could work in conjunction with a xanalogical storage system.
+For example, a presentation layer could specify font sizes, links, or annotations, and multiple layers could be stacked when rendering a particular piece of content.
+Given \tw's data model and presentation code, adding layers would not be difficult.
+In fact, particular types of layers are already implemented:  highlights for misspellings, quote context, and hit search terms are applied to document text after it is assembled.
+Highlights are achieved by inserting presentation tags (in this case, HTML font color tags) around particular character spans.
+Many other presentation styles could be supported with a similar mechanism by inserting other tag types.
+Layers are an ideal feature to add in a future development iteration.
 

### 2003-02-13 papers/hypertext2003/paper.tex
Spell-checked.

@@
 % Created.
+%
+% 2003-February-13 Jason Rohrer
+% Finished initial draft.
+% Spell-checked.
 %
@@
 
-Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \ was implented from scratch in ten days by one person.  
+Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \  was implemented from scratch in ten days by one person.  
 We attribute this success to the maturity of modern technology and development techniques.  
@@
 will be a product.  And by 1995 it will begin to change the world.
-Much work remains to be done to realise the potential of Xanadu---it
+Much work remains to be done to realize the potential of Xanadu---it
 will take the Xanadu development team 18 months to field the first
@@
 The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
-We can look at architecture diagrams and photgraphs of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
+We can look at architecture diagrams and photographs of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
 Few of us have ever played with a xanalogical user interface prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
@@
 Third, this paper describes a full xanalogical system implementation from the perspective of an end-user.
-The novelty of this paper hinges on the implmentation, which has a modern flavor, though the underlying ideas are quite old.
-We have acheived a novel success, where past attempts have failed, and we feel that the lessons learned from this process are valuable.
+The novelty of this paper hinges on the implementation, which has a modern flavor, though the underlying ideas are quite old.
+We have achieved a novel success, where past attempts have failed, and we feel that the lessons learned from this process are valuable.
 
@@
 When document $A$ transcludes a quote from document $B$, the quote is stored as a deep reference to the quoted material in $B$:  words from $B$ are not copied into $A$. 
-Whenver $A$ is viewed, the words from $A$ are fetched from $A$'s owner, and the necessary words from $B$ are fetched from $B$'s owner.
+Whenever $A$ is viewed, the words from $A$ are fetched from $A$'s owner, and the necessary words from $B$ are fetched from $B$'s owner.
 Thus, even though $A$'s owner has quoted document $B$, the quoted owner still retains control over the distribution and licensing of his or her words.
@@
 We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days.
-To acheive this kind of rapid development, we relied heavily on modern technology and design techniques.
+To achieve this kind of rapid development, we relied heavily on modern technology and design techniques.
 We do not view past Xanadu failures with disdain.
@@
 Our system, though full-featured, was not designed to be ``the'' scalable xanalogical system that will carry us all into the future.
-Instead, we focused on building a usable implemenation of xanalogical features for the purpose of experimentation.
-Though scalability was not a design goal, \tw \ was built on top of technolgies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
+Instead, we focused on building a usable implementation of xanalogical features for the purpose of experimentation.
+Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
 We claim that \tw \   could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.
@@
 By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
-%When following a quote reference, a chain of referneces may need to be chased before the original context of the text is found.
+%When following a quote reference, a chain of references may need to be chased before the original context of the text is found.
 
@@
 %By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
-%When a new chunk is created as part of a document, the context portion of the reference is ommited, indicating that the document is the first context in which this chunk was used.
+%When a new chunk is created as part of a document, the context portion of the reference is omitted, indicating that the document is the first context in which this chunk was used.
 

### 2003-02-13 papers/hypertext2003/paper.tex
Finished first round of proof reading.

@@
 % Spell-checked.
+% Finished first round of proof reading.
 %
@@
 Given this historical perspective, the contributions of this paper are threefold.
-First, this paper analyzes the process that lead from a paper design to real world xanalogical software.
+First, this paper analyzes the process that lead from a paper design to real-world xanalogical software.
 Second, this paper shows that modern technology and techniques are of utmost importance for making this implementation process {\it possible}, let alone quick.
@@
 Thus, as $B$ is updated, all previous versions are maintained, and $A$'s quote can point to the particular version that $A$'s owner quoted.
-A particular version of $B$ is immutable, so $A$'s quote will never break.
+Each version of $B$ is immutable, so $A$'s quote will never break.
 
@@
 In practice, an author will need to read a document before quoting it, but this reading requires only the normal first-access payment, no matter how widely the new, quoting document is expected to be read.
-In fact, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
+However, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
 Thus, authors benefit from the unrestricted quotation and reuse of their work:  they have no financial motivation for imposing any limits.
@@
 We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days.
-To achieve this kind of rapid development, we relied heavily on modern technology and design techniques.
+To achieve this kind of rapid development, we relied heavily on modern technology and development techniques.
 We do not view past Xanadu failures with disdain.
@@
 Our system, though full-featured, was not designed to be ``the'' scalable xanalogical system that will carry us all into the future.
-Instead, we focused on building a usable implementation of xanalogical features for the purpose of experimentation.
+Instead, we focused on building a usable implementation of core xanalogical features for the purpose of experimentation.
 Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
-We claim that \tw \   could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.
+Given these precedents, we believe that \tw \   could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.
 
@@
 In describing the \tw \  user experience, we are faced with the very issue that motivated \tw \  development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to {\it use} a system.
-Since this paper's focus is on a real-world implementation and not just a paper description, we encourage readers to visit {\tt http://hypertext.sf.net/token\_word} to try our system for themselves.
+Since this paper's focus is on a real-world implementation and not just an abstract description, we encourage readers to visit {\tt http://hypertext.sf.net/token\_word} to try our system for themselves.
 
@@
 Quote markers can be hidden or displayed, and quotes can be followed to see the context from which they were taken.
-Each document also features a list of documents that quote it, so references can be chased in both directions.
+Each document also features a list of documents that quote it, so references can be followed in both directions.
 The \tw \   document display interface can be seen in Figure \ref{fig:mainScreen}.
@@
 Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
-Quotes on a clipboard can be followed to see quote context.
+Quote references on a clipboard can be followed to see a quote's context.
 The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
@@
 
-Full text searches are supported across the entire document database, and search terms are highlighted when result documents are displayed.
+Full text searches are supported across the entire document space, and search terms are highlighted when result documents are displayed.
 Search results (and other lists in \tw) are sorted with most-quoted documents first, since frequently quoted documents are likely to contain the best information.
+This ranking mechanism is similar to Google's PageRank algorithm \cite{Brin1998}.
 
-\tw \  provides no explicit linking mechanism.
-However, since quote context can be obtained easily, brief quotes can be used as links between documents.
-For an example of quotes used to link, see Figure \ref{fig:quotesAsLinks}.
+\tw \  provides no explicit document linking mechanism.
+However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
+For an example of quotes used as links, see Figure \ref{fig:quotesAsLinks}.
 
@@
 \epsfig{file=images/quotesAsLinks.eps, width=20pc}
-\caption{Brief portions of documents can be quoted to form links.}
+\caption{Brief portions of documents can be quoted to emulate links.}
 \label{fig:quotesAsLinks}
@@
 There are two types of data objects in \tw:  documents and chunks.
-A chunk contains a raw block of contiguous text, while a document is a list of reference to text chunks.
+A chunk contains a raw block of contiguous text, while a document is a list of references to text chunks.
 Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.
 
-Each reference in a document contains a pointer to text chunk region and an optional pointer to a document context region.
+Each reference in a document contains a pointer to a text chunk region and an optional pointer to a document context region.
 The document context pointer tracks which document the material was quoted from and is used for quote reference chasing.
 If a document refers to a new text chunk that has not appeared in any previous documents, the document context pointer is omitted:  such chunks are not part of quotes and have no references that can be chased.
-With this two-pointer model, we can distinguish ``original'' material in a document from quoted material and support recursive reference chasing.
-By following context repeatedly for a nested quotation, the original author and document context of particular words can be obtained.
+With this two-pointer model, we can distinguish ``original'' material in a document from quoted material.  % and support recursive reference chasing.
+By following references recursively for a nested quotation, the original author and document context of particular words can be obtained.
 %When following a quote reference, a chain of references may need to be chased before the original context of the text is found.
 
-For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote original material, residing in chunk $k$, from document $C$.  
+For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote of original material, residing in chunk $k$, from document $C$.  
 $A$'s reference will contain both a pointer to the text chunk $k$ and to the document context $B$.  
@@
 At the end of this reference chain, $C$'s reference will point only to $k$.
-Figure \ref{fig:referenceChain} shows a diagram of this reference chain.
+Figure \ref{fig:referenceChain} shows a diagram of our model applied to this reference chain.
 
@@
 
-\dirbow{kInCStartAnchor}{kStartAnchor}{.17}[\grapharrowtype{1}]
-\dirbow{kInCEndAnchor}{kEndAnchor}{.17}[\grapharrowtype{1}]
+\dirbow{kInCStartAnchor}{kStartAnchor}{.17}[\grapharrowtype{1}\graphlinecolour{0.65}]
+\dirbow{kInCEndAnchor}{kEndAnchor}{.17}[\grapharrowtype{1}\graphlinecolour{0.65}]
 
@@
 Light gray regions represent text from chunk $k$.
-Dark gray regions in $A$ and $B$ represent portions of $A$'s quote from $B$ that do not come from chunk $k$ (other chunks are omitted from this diagram for clarity).}
+Dark gray regions in $A$ and $B$ represent portions of $A$'s quote from $B$ that do not come from chunk $k$ (other chunks have been omitted from this diagram).
+Arcs between $C$ and $k$ have been colored gray for clarity.}
 \label{fig:referenceChain}
@@
 
-Quote clipboards are modeled in the following way.
+Quote clipboards are modeled like documents, but with minor differences.
 Each quote on the clipboard points to a contiguous document region.
@@
 To insert a clipboard quote into a new document, we can resolve the chunk region references for the quote and set the document region for each of these references to the document from which the quote was extracted.
-This model allows us both to track the extraction context of the quote and to store the quote clipboard efficiently.
+This simple model allows us both to track the extraction context of the quote and to store the quote clipboard efficiently.
 Figure \ref{fig:quoteClipboardModel} shows a diagram of a quote clipboard modeled in this way.
@@
 \begin{center}
-{\tt <chunkUserID, chunkID, startOffset, length;\\ 
-docUserID, docID, startOffset>} 
+{\tt <chunkUserID, chunkID, chunkStartOffset, length;\\ 
+docUserID, docID, docStartOffset>} 
 \end{center}
@@
 Even though the full development cycle was short, we used an iterative process.
-Features were added one at a time to the system, and the system was maintained in a usable form at all times.
-For example, we started with a system that managed text chunks, then added document management, then added quotes, then added tokens transfers, {\it etc.}
+Features were added one at a time to \tw, and the system was maintained in a usable form at all times.
+For example, we started with a system that managed text chunks, then added document management, then added quotes, and then added tokens transfers.
 Final iterations added features such as spell checking and index-based searching.
@@
 The first limitation is in terms of storage efficiency:  most filesystems have a minimum file size, and this minimum is usually larger than 1 kilobyte.
-In our example, 33 bytes of data would occupy at least a kilobyte of disk space.
+In our example, 33 bytes of document data would occupy at least a kilobyte of disk space.
 
-The second limitation is in terms of filesystem architecture:  Unix-like filesystems use an inode table, and each file must be associated with an inode.
+The second limitation is in terms of filesystem architecture:  Unix-like filesystems use an inode table, and each file must be associated with a unique inode.
 When a filesystem is created, the number of available inodes is fixed, and this number can be relatively small (the common ratio for modern Linux systems seems to be about 200,000 inodes per gigabyte of disk space).
@@
 A second approach would be to implement a simple application-level virtual filesystem for chunk and document storage.
-With this approach, we could taylor the storage system to our specific needs, though it would certainly be labor-intensive.
+With this approach, we could taylor the storage system to our specific needs, though its development would certainly be labor-intensive.
 
@@
 A scalable backend might be seen as a feature to be added in a future iteration.
-Our system, in its current form, is still functional in terms of its goals:  it can potentially support hundreds of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
+Our system, in its current form, is still functional in terms of its goal:  it can potentially support thousands of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
 
@@
 Similarly, withdrawing tokens in exchange for real-world currency is not frictionless: 
-PayPal does not support an automated payment mechanism, so withdrawl requests are queued for manual processing by the \tw \  system administrator.
+PayPal does not support an automated payment mechanism, so withdrawl requests must be queued for manual processing by the \tw \  system administrator.
 Whereas deposits take effect immediately (using PayPal's ``Instant Payment Notification'' service), withdrawn token refunds are delayed by the response of the human administrator.
@@
 Given that micropayments in \tw \  are mandatory and automatic, a major barrier to system adoption might exist:  trying \tw \  would require the deposit of real-world currency.
-Even the main page displayed after login is a first-class \tw \  document, so a new user with no tokens would not be able to read a description of \tw, let alone try any of its features.
+Even the main page displayed after login is a first-class \tw \  document, so a new user with no tokens would not even be able to read a description of \tw, let alone try any of its features.
 
@@
 The second type of tokens, called {\it real} tokens, can be exchanged for real-world currency.
-Token transfers inside \tw \  keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
+The token transfer logic in \tw \  keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
 Trial tokens are favored, and real tokens are only spent when a user has no trial tokens.
 
-For example, suppose the balances of three users are as shown in following table:
+For example, suppose that the balances of three users are as shown in following table:
 %suppose user $A$ has a trial:real token balance of 50:200, user $B$ has a balance of 0:500, and user $C$ has a balance of 10:0.
@@
 \hline
-$B$&50  &520\\
+$B$&50  &530\\
 \hline
@@
 This two-type scheme allows users to try \tw \  extensively without a monetary investment, and it also poses no financial risks to the administrators.
-Note that though trial tokens have no real-world value, they still have value inside \tw, since they can always be used to purchase new content.
-Inside \tw, a user that amasses many trial tokens is just as wealthy as a user with many real tokens.
+Note that though trial tokens have no real-world value, they still have value in \tw, since they can always be used to purchase new content.
+Inside \tw, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
 A user that actively published popular content in \tw \  could effectively use the system forever without depositing any real-world money.
@@
 Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}, so we will focus on related non-xanalogical systems here.
-However, we should mention that interest in xanalogical systems has not waned in recent years.
+However, we should mention that interest in Xanadu has not waned in recent years.
 For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
@@
 
-Aside from the sociological issues, Wikis approach hypertext in an interesting way.
-Links can be created in a document to documents that do not exist without knowing where those documents will eventually reside.
+Despite the fact that their sociological aspects receive most of the attention, Wikis are also interesting from a hypertext perspective.
+Links can be created to documents that do not yet exist without knowing where those documents will eventually reside.
 To create a new document, a user must follow one of these dangling links in an existing page, which leads to a page creation screen.
@@
 
-\tw \  differs from a Wiki in its approach to hypertext, since a \tw \  quote can only be taken from an existing document.
-No mechanism is provided for refering to a document that does not yet exist.
+%\tw \  differs from a Wiki in its approach to hypertext, since a \tw \  quote can only be taken from an existing document.
+%No mechanism is provided for refering to a document that does not yet exist.
 
-The first Wiki was created by Ward Cunningham in 1995 and is still active today\cite{WikiWikiWeb}.
+The first Wiki was created by Ward Cunningham in 1995 and is still active today \cite{WikiWikiWeb}.
 The most ambitious Wiki-based project is Wikipedia, a user-edited encyclopedia, which recently grew to over 100,000 entries \cite{Wikipedia}.
@@
 \subsection{Everything2}
-Like \tw \  and Wikis, Everything2 is a web-based hypertext system implemented using CGI and Perl \cite{Everything2}.
+Like \tw \  and Wikis, Everything2 \cite{Everything2} is a web-based hypertext system implemented using CGI and Perl.
 Everything2 supports dangling links to pages that do not exist yet, but it handles these links differently than a Wiki does.
-When a user follows a dangling link, a search is performed for the title of the non-existant page.
-Thus, dangling links are fuctional from a reader's point of view.
-We might conclude that Wikis favor authors, while Everything2 favors readers.
-As soon as a page is created that matches the title of a dangling link, that link points to the new page directly.
+When a user follows a dangling link, a search is performed for the title words of the non-existant page.
+Thus, dangling links are more fuctional in Everything2 from a reader's point of view.
+Using this comparison point, we might conclude that Wikis favor authors, while Everything2 favors readers.
+%As soon as a page is created that matches the title of a dangling link, that link points to the new page directly.
 
@@
 These systems allow content to be added to a web site serially, one post at a time.
-Some blogs are used by individuals as a means of sharing daily thoughts with the world, while others aim to be collaborative information spaces filled with moderated comments posted by the public.
+Some blogs are used by individuals as a means of sharing daily thoughts with the world, while others aim to be collaborative information spaces and feature moderated comments posted by the public.
 One of the most interesting collaborative weblogs is Kuro5hin (pronounced ``corrosion''), which features high-quality news and culture stories submitted and moderated by the public \cite{kuro5hin}.
@@
 One additional strategy was crucial, though it has not been mention explicitly:  a focus on a core xanalogical feature set.
-We set out to build a system that supported deep quotation, unbreakable references, and frictionless micropayments.
-In Section \ref{sec:Xanadu}, we distilled these features from the Xanadu model.
-However, {\it Literary Machines} is over 250 pages long, and it is choked full of features that an ideal xanalogical system might have \cite{NelsonLiteraryMachines}.
-Perhaps previous Xanadu efforts aimed for this ideal feature set, and perhaps this is why they failed.
+We aimed to build a system that supported deep quotation, unbreakable references, and frictionless micropayments---we distilled these features from the Xanadu model in Section \ref{sec:Xanadu}.
+However, {\it Literary Machines} is over 250 pages long, and it is chocked full of features that an ideal xanalogical system might have \cite{NelsonLiteraryMachines}.
+Perhaps previous Xanadu efforts aimed to support this entire feature set, and perhaps that is why they failed.
 
-\tw \  is by no means the ideal xanalogical system, and many features are missing.
+\tw \  is by no means an ideal xanalogical system, and many features are missing.
 However, it is still the first system to implement the core features of the Xanadu architecture.
@@
 Second, \tw \  does not support multi-server integration:  each installation of \tw \  operates in isolation, and quotes between documents at different sites are not possible.
-We see multi-server integration as one of the weakpoints in the Xanadu model:  how can we ensure that references never break in a system comprised of multiple, separately owned servers?
+We see multi-server integration as one of the weakpoints in the Xanadu architecture:  how can we ensure that references never break in a system comprised of multiple, separately owned servers?
 Even if fault-tolerant, multi-server integration is possible, it is not essential for the end-user experience. 
-Third, \tw \   does not support the side-by-side document comparission with {\it transpointing} lines, a classic Xanadu feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
+Third, \tw \   does not support side-by-side document comparission with {\it transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
 The transpointing interface would be difficult, if not impossible, to support in a web browser with no additional software.
@@
 For example, a presentation layer could specify font sizes, links, or annotations, and multiple layers could be stacked when rendering a particular piece of content.
-Given \tw's data model and presentation code, adding layers would not be difficult.
+Given \tw's current data model and presentation logic, adding layers would not be difficult.
 In fact, particular types of layers are already implemented:  highlights for misspellings, quote context, and hit search terms are applied to document text after it is assembled.
 Highlights are achieved by inserting presentation tags (in this case, HTML font color tags) around particular character spans.
-Many other presentation styles could be supported with a similar mechanism by inserting other tag types.
+Many other presentation styles could be supported in this way by inserting other tag types.
 Layers are an ideal feature to add in a future development iteration.

### 2003-02-15 papers/hypertext2003/paper.tex
Made changes to match ACM SIG formatting guidelines.

@@
+% 
+% token_word paper
+% Author:  Jason Rohrer
+%
+
 %
@@
 % Finished first round of proof reading.
+%
+% 2003-February-14 Jason Rohrer
+% Made changes to match ACM SIG formatting guidelines.
 %
@@
 }
-
-\date{February 6, 2003}
 
@@
 
-That question by itself, the impossibility question, is extraordinarily intriguing.  We {\it know} that Xanadu is not impossible.  
+That question by itself, the impossibility question, is extraordinarily intriguing.  We \textit{know} that Xanadu is not impossible.  
 The design, on paper \cite{NelsonLiteraryMachines}, is clear enough:  we just need to build it.  
@@
 Will anyone argue that Autodesk did not have extraordinary software development resources in the late 1980s?  
-Furthermore, Autodesk {\it believed} in Xanadu.  
+Furthermore, Autodesk \textit{believed} in Xanadu.  
 The following quote from a 1988 Autodesk press release is most telling:
@@
 We hear its siren song and are tempted, but we know that many have tried and many have failed.  
-The most frustrating factor is that none of us really know how useful Xanadu would be, even if it {\it did} exist.  
+The most frustrating factor is that none of us really know how useful Xanadu would be, even if it \textit{did} exist.  
 We can look at architecture diagrams and photographs of cardboard mock-ups \cite{Nelson1999}, but these do not give us a true sense of what it would be like to use a xanalogical system.  
@@
 First, this paper analyzes the process that lead from a paper design to real-world xanalogical software.
-Second, this paper shows that modern technology and techniques are of utmost importance for making this implementation process {\it possible}, let alone quick.
+Second, this paper shows that modern technology and techniques are of utmost importance for making this implementation process \textit{possible}, let alone quick.
 Third, this paper describes a full xanalogical system implementation from the perspective of an end-user.
@@
 As mentioned in the above quote, Xanadu's underlying ideas were first incubated by Nelson in the 1960s \cite{Nelson1965}.  
-These ideas evolved somewhat over the next forty years, receiving one of their most verbose presentations in Nelson's book {\it Literary Machines}, which was first published in 1981 \cite{NelsonLiteraryMachines}.
+These ideas evolved somewhat over the next forty years, receiving one of their most verbose presentations in Nelson's book \textit{Literary Machines}, which was first published in 1981 \cite{NelsonLiteraryMachines}.
 Nelson's more recent paper on the xanalogical model is up to date in terms of modern technological trends, but the core ideas have not changed \cite{Nelson1999}.  
-The high-level description and interpretation of Xanadu given here is based on information culled from {\it Literary Machines}, Nelson's recent lectures, and personal conversations with Nelson.
+The high-level description and interpretation of Xanadu given here is based on information culled from \textit{Literary Machines}, Nelson's recent lectures, and personal conversations with Nelson.
 
-The chief goal of Xanadu, distilled into a single phrase, is {\it frictionless content reuse}.  
+The chief goal of Xanadu, distilled into a single phrase, is \textit{frictionless content reuse}.  
 This goal would be easily realized in a frictionless, copyright-free world:  authors could simply copy whatever they want and reuse it however they please.  
@@
 All of the design choices and complications in the Xanadu model can be seen as mechanisms for making reuse frictionless in the face of copyright.
-When trying to implement unrestricted reuse in a way that works with copyright, we are faced with the following issue:  {\it copyright forbids unrestricted copying}.
+When trying to implement unrestricted reuse in a way that works with copyright, we are faced with the following issue:  \textit{copyright forbids unrestricted copying}.
 
-Xanadu's central mechanism is {\it transclusion}, a form of quotation.  
+Xanadu's central mechanism is \textit{transclusion}, a form of quotation.  
 Transclusion differs from standard quotation in that it does not involve copying of any kind.  
@@
 The Xanadu model handles this licensing issue with micropayments and per-character values for content.
-Nelson is fond of using the term {\it nanobuck} ($10^{-9}$ dollars) to describe the smallest unit of payment:  documents, or portions of documents, are licensed for $N$ nanobucks per character.
+Nelson is fond of using the term \textit{nanobuck} ($10^{-9}$ dollars) to describe the smallest unit of payment:  documents, or portions of documents, are licensed for $N$ nanobucks per character.
 For example, if $N=100$, a document containing one million characters, if licensed in its entirety, would cost \$0.10, while the first half would cost only \$0.05.
@@
 \subsection{User Perspective}
-In describing the \tw \  user experience, we are faced with the very issue that motivated \tw \  development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to {\it use} a system.
-Since this paper's focus is on a real-world implementation and not just an abstract description, we encourage readers to visit {\tt http://hypertext.sf.net/token\_word} to try our system for themselves.
+In describing the \tw \  user experience, we are faced with the very issue that motivated \tw \  development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to \textit{use} a system.
+Since this paper's focus is on a real-world implementation and not just an abstract description, we encourage readers to visit \texttt{http://hypertext.sf.net/token\_word} to try our system for themselves.
 
@@
 \begin{center}
-{\tt <chunkUserID, chunkID, chunkStartOffset, length;\\ 
+\texttt{<chunkUserID, chunkID, chunkStartOffset, length;\\ 
 docUserID, docID, docStartOffset>} 
@@
 The second portion, which is optional, describes the document region context of the reference.  
-Note that {\tt chunkUserID} may differ from {\tt docUserID}, since the quoted region may itself be part of a quote in the context document (in the case of a nested quote).
-Consider our previous example, which is shown in Figure \ref{fig:referenceChain}, and suppose that documents $B$ and  $C$ are owned by {\tt userY} and {\tt userZ}, respectively.
+Note that \texttt{chunkUserID} may differ from \texttt{docUserID}, since the quoted region may itself be part of a quote in the context document (in the case of a nested quote).
+Consider our previous example, which is shown in Figure \ref{fig:referenceChain}, and suppose that documents $B$ and  $C$ are owned by \texttt{userY} and \texttt{userZ}, respectively.
 %For example, document $A$ may quote from document $B$, but the portion that $A$ quotes may be part of $B$'s quote from document $C$.
@@
 \begin{center}
-{\tt <userZ, k, 12, 50; userY, B, 125>} 
+\texttt{<userZ, k, 12, 50; userY, B, 125>} 
 \end{center}
 In other words, we have 50 characters from chunk $k$, starting with character 13, which were quoted from document $B$, starting at character 126.
-{\tt userZ} owns both document $C$ and chunk $k$, since $k$ was created as original material for use in $C$.
-Note that {\tt length} is not specified for the document region context of a reference, since it would be redundant (in our example, it would be 50).
+\texttt{userZ} owns both document $C$ and chunk $k$, since $k$ was created as original material for use in $C$.
+Note that \texttt{length} is not specified for the document region context of a reference, since it would be redundant (in our example, it would be 50).
 
@@
 \begin{center}
-{\tt <docUserID, docID, startOffset, length>} 
+\texttt{<docUserID, docID, startOffset, length>} 
 \end{center}
-Consider our previous example clipboard, which is shown in Figure \ref{fig:quoteClipboardModel}, and suppose that documents $A$ and  $B$ are owned by {\tt userX} and {\tt userY}, respectively.
+Consider our previous example clipboard, which is shown in Figure \ref{fig:quoteClipboardModel}, and suppose that documents $A$ and  $B$ are owned by \texttt{userX} and \texttt{userY}, respectively.
 The clipboard representation might look like this:
 \begin{center}
-{\tt <userX, A, 37, 75>}\\
-{\tt <userY, B, 100, 50>}\\ 
+\texttt{<userX, A, 37, 75>}\\
+\texttt{<userY, B, 100, 50>}\\ 
 \end{center}
@@
 Our approach uses two token types.
-The first type of tokens, called {\it trial} tokens, have no real-world value.
+The first type of tokens, called \textit{trial} tokens, have no real-world value.
 Each new account starts out with a small number of trial tokens (in our live system, each account starts with 50,000 trial tokens).
-The second type of tokens, called {\it real} tokens, can be exchanged for real-world currency.
+The second type of tokens, called \textit{real} tokens, can be exchanged for real-world currency.
 The token transfer logic in \tw \  keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
@@
 We aimed to build a system that supported deep quotation, unbreakable references, and frictionless micropayments---we distilled these features from the Xanadu model in Section \ref{sec:Xanadu}.
-However, {\it Literary Machines} is over 250 pages long, and it is chocked full of features that an ideal xanalogical system might have \cite{NelsonLiteraryMachines}.
+However, \textit{Literary Machines} is over 250 pages long, and it is chocked full of features that an ideal xanalogical system might have \cite{NelsonLiteraryMachines}.
 Perhaps previous Xanadu efforts aimed to support this entire feature set, and perhaps that is why they failed.
@@
 Even if fault-tolerant, multi-server integration is possible, it is not essential for the end-user experience. 
-Third, \tw \   does not support side-by-side document comparission with {\it transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
+Third, \tw \   does not support side-by-side document comparission with \textit{transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
 The transpointing interface would be difficult, if not impossible, to support in a web browser with no additional software.
@@
 ``Xanadu'' is a trademark of Ted Nelson.
-To prevent confusion, the generic terms ({\it e.g.}, xanalogical system) have been used wherever possible.
+To prevent confusion, the generic terms (\textit{e.g.}, xanalogical system) have been used wherever possible.
 

### 2003-02-15 papers/hypertext2003/paper.tex
Added changes in response to Jim's comments.

@@
 %
+% 2003-February-15 Jason Rohrer
+% Added changes in response to Jim's comments.
+%
 
@@
 
-\title{\tw:  Building a Xanalogical System in Ten Days}
+\title{\tw:  a Xanalogical Storage and Authoring System}
 
@@
 Furthermore, \tw \  is the first xanalogical system of any kind to be accessible by a web browser with no additional software.
+Previous attempts at full xanalogical implementations took many years and were ultimately never completed.
+Given this historical backdrop, an additional contribution of this paper is in analyzing the development strategies that led to a relatively novel success.
+A live \tw \  system is running at:
 
-Though previous attempts at xanalogical implementations took many years and ultimately were never completed, \tw \  was implemented from scratch in ten days by one person.  
-We attribute this success to the maturity of modern technology and development techniques.  
-%In particular, choosing Perl as the implementation language allowed the rather complex xanalogical text processing operations to be expressed in elegant ways.
-A live \tw \  system is running at:
-\begin{center}
-http://hypertext.sf.net/token\_word
-\end{center}
+\centering\texttt{http://hypertext.sf.net/token\_word}
+
 \end{abstract}
@@
 Few of us have ever played with a xanalogical user interface prototype, even fewer have paid or received a true micropayment (xanalogical or otherwise), and almost none have transcluded the work of another or had our work transcluded.
+Many hypertext systems have been inspired by xanalogical ideas.
+To our knowledge, however, none of these system support a true form of transclusion, let alone transclusion \textit{and} micropayments, both of which are central to the Xanadu architecture and user experience.
 
@@
 \section{System Architecture}
-We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days.
+We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days, and our development team consisted of a single programmer.
 To achieve this kind of rapid development, we relied heavily on modern technology and development techniques.
@@
 For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
+Recent work with XLink has focused on adding transclusion capabilities to the web \cite{Lowe2001}, but support is limited to embedding entire documents.
+XPointer can be used in conjunction with XLink to refer to document spans \cite{Vitali2002}, though nothing prevents these references from breaking when documents change.
 

### 2003-02-15 papers/hypertext2003/paper.tex
More changes in response to Jim's comments.

@@
 Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
-Given these precedents, we believe that \tw \   could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.
+Given these precedents, our architecture could potentially be scalled to support large document collections.
+Section \ref{sec:Scalability} discusses these scalability issues in more detail.
 
@@
 Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
+To extract a document region as a quote, the user inserts $<$\texttt{q}$>$ $<$$/$\texttt{q}$>$ tags around the desired region in a text area.
+This interaction mechanism is arguably more elegant and less error-prone than mouse-based selection highlighting, especially when extracting large regions that span several screens full of text.
 Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
-Quote references on a clipboard can be followed to see a quote's context.
+Each quote is assigned a $<$\texttt{q N}$>$ tag to be used when inserting the quote into new documents---$<$\texttt{q 3}$>$ refers to the quote at index three on the clipboard.
+The use of these abreviated handles hides the complexity of references and document regions from the user.
+After extracting a quote, the user never needs to deal directly with the document region again, though the original context of a quote can be seen with a single click from the quote clipboard.
 The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
-When creating a new document, a user can enter new text along with references to quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
+When creating a new document, a user can enter new text along with handle tags for quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
 A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.
@@
 \epsfig{file=images/quoteClipboard.eps, width=20pc}
-\caption{The quote clipboard interface.}
+\caption{The quote clipboard interface.  Each quote is associated with a $<$\texttt{q N}$>$ reference tag, where \texttt{N} is the quote's index on the clipboard.}
 \label{fig:quoteClipboard}
 \end{figure}
+
+Figures \ref{fig:extractQuote} through \ref{fig:docPreview} show a sequence of actions from a common usage scenareo:  extracting a quote, viewing the quote on the clipboard, creating a new document that uses the quote, and previewing the document.
+After correcting the spelling mistake highlithed in Figure \ref{fig:docPreview}, the final step would be to submit the document.
+Once submitted, the work becomes a full-fledged \tw \  document, making it readable and quotable by other users in the system.
 
@@
 However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
+For example, to link to a target document called ``frequently asked questions,'' the title words of the document can be quoted.
+When quote markers are shown in the linking document, the words ``frequently asked questions'' will be marked, and clicking on the words will lead to the context of the quote (in other words, to the target document ``frequently asked questions'').
+If the title words are not appropriate for use as a link anchor, another more relevant phrase from the body of the target document can be quoted to form a link.
 For an example of quotes used as links, see Figure \ref{fig:quotesAsLinks}.
@@
 \epsfig{file=images/quotesAsLinks.eps, width=20pc}
-\caption{Brief portions of documents can be quoted to emulate links.}
+\caption{Brief portions of documents can be quoted to emulate links.  Here, the titles of two documents, ``frequently asked questions'' and ``\tw \  history,'' have been quoted.}
 \label{fig:quotesAsLinks}
@@
 %When following a quote reference, a chain of references may need to be chased before the original context of the text is found.
-
-For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote of original material, residing in chunk $k$, from document $C$.  
-$A$'s reference will contain both a pointer to the text chunk $k$ and to the document context $B$.  
-$B$'s reference will point to both chunk $k$ and document $C$.  
-At the end of this reference chain, $C$'s reference will point only to $k$.
-Figure \ref{fig:referenceChain} shows a diagram of our model applied to this reference chain.
 
@@
 \end{figure*}
+
+For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote of original material, residing in chunk $k$, from document $C$.  
+$A$'s reference will contain both a pointer to the text chunk $k$ and to the document context $B$.  
+$B$'s reference will point to both chunk $k$ and document $C$.  
+At the end of this reference chain, $C$'s reference will point only to $k$.
+Figure \ref{fig:referenceChain} shows a diagram of our model applied to this reference chain.
 
@@
 \subsubsection{Scalability Limitations}
+\label{sec:Scalability}
 The main scalability limitation of our implementation is the use of a filesystem as a data backend.
@@
 \bibliography{paper}
+
 \end{document}

### 2003-02-15 papers/hypertext2003/paper.tex
Added more changes per Jim's comments.

@@
 A scalable backend might be seen as a feature to be added in a future iteration.
-Our system, in its current form, is still functional in terms of its goal:  it can potentially support thousands of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.
+Our system, in its current form, is still functional in terms of its goal, which is to support exploration of a multi-user xanalogical system.
 
@@
 From the administrator's point of view, the withdrawl queue can be used to increase security, since any suspicious activity can be investigated before real-world payments are made.
+
+In our live system, we chose an exchange rate of 1,000,000 tokens for \$1, though this parameter can be changed on a site-by-site basis.
+With this exchange rate, we tried to minimize financial burden on readers while still assigning appreciable value to content.
+For example, the full text of this paper would cost about \$0.04, so 25 people would need to read it before it earned \$1 worth of tokens.
 
@@
 Suppose that user $A$ reads a new 100-chracter document that is owned by $B$, but that the document contains a 20-character quote by $C$.
+User $A$ must pay 100 tokens to access this new content, with 80 going to $B$ and 20 going to $C$.
+The transfer logic favors trial tokens, so $A$'s trial balance is exhausted first by transfering 50 tokens to $B$.
+The remaining payment to $B$ is made with 30 real tokens, and 20 real tokens are also transfered to $C$.
 The resulting balances are shown in the following table:
@@
 Inside \tw, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
-A user that actively published popular content in \tw \  could effectively use the system forever without depositing any real-world money.
+A user that actively publishes popular content in \tw \  could effectively use the system forever without depositing any real-world money.
 

### 2003-02-15 papers/hypertext2003/paper.tex
Finished changes in response to Jim's comments.

@@
 Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}, so we will focus on related non-xanalogical systems here.
-However, we should mention that interest in Xanadu has not waned in recent years.
+
+However, we should mention that interest in Xanadu has not waned in recent years, even though development work on Udanax, the last official (and most ambitious) Xanadu implementation effort, ceased in 1995 \cite{Udanax}.
 For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
-Recent work with XLink has focused on adding transclusion capabilities to the web \cite{Lowe2001}, but support is limited to embedding entire documents.
+As another example, recent work with XLink has focused on adding transclusion capabilities to the web \cite{Lowe2001}, but support is limited to embedding entire documents.
 XPointer can be used in conjunction with XLink to refer to document spans \cite{Vitali2002}, though nothing prevents these references from breaking when documents change.
@@
 \section{Conclusion}
-Thoughout this paper, we have discussed the strategies that made \tw \  development possible, including an interative process and heavy use of existing technology.
+Thoughout this paper, we have discussed the strategies that made \tw \  development possible, including an iterative process and heavy use of existing technology.
 

### 2003-02-15 papers/hypertext2003/paper.tex
Changed title.
Spell-checked.

@@
 % Added changes in response to Jim's comments.
+% Spell-checked.
 %
@@
 
-\newcommand{\tw}{token\_word}
+\newcommand{\tokenWord}{token\_word}
 
@@
 
-\title{\tw:  a Xanalogical Storage and Authoring System}
+\title{\tokenWord:\\a Xanalogical Transclusion and Micropayment System}
 
@@
 \begin{abstract}
-We describe \tw, a web-based xanalogical hypertext system.  
+We describe \tokenWord, a web-based xanalogical hypertext system.  
 Our system supports almost every core feature associated with Xanadu, an architecture that has been actively discussed for nearly forty years.
 Features include deep quotation, unbreakable references, two-way reference chasing, and frictionless micropayments that are backed by real-world currency.
-To our knowledge, \tw \ is the first xanalogical system implementation to included all of these features.
-Furthermore, \tw \  is the first xanalogical system of any kind to be accessible by a web browser with no additional software.
+To our knowledge, \tokenWord \  is the first xanalogical system implementation to included all of these features.
+Furthermore, \tokenWord \  is the first xanalogical system of any kind to be accessible by a web browser with no additional software.
 Previous attempts at full xanalogical implementations took many years and were ultimately never completed.
 Given this historical backdrop, an additional contribution of this paper is in analyzing the development strategies that led to a relatively novel success.
-A live \tw \  system is running at:
+A live \tokenWord \  system is running at:
 
@@
 \section{System Architecture}
-We designed and built \tw, a full-featured xanalogical system, from scratch in only ten days, and our development team consisted of a single programmer.
+We designed and built \tokenWord, a full-featured xanalogical system, from scratch in only ten days, and our development team consisted of a single programmer.
 To achieve this kind of rapid development, we relied heavily on modern technology and development techniques.
@@
 Those early attempts were simply ahead of their time:  the technology of the day was not ready for Xanadu.
-The central technologies that made \tw \   development possible were the web, CGI, Perl, and PayPal \cite{paypal}.
+The central technologies that made \tokenWord \   development possible were the web, CGI, Perl, and PayPal \cite{paypal}.
 
@@
 Instead, we focused on building a usable implementation of core xanalogical features for the purpose of experimentation.
-Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
-Given these precedents, our architecture could potentially be scalled to support large document collections.
+Though scalability was not a design goal, \tokenWord \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
+Given these precedents, our architecture could potentially be scaled to support large document collections.
 Section \ref{sec:Scalability} discusses these scalability issues in more detail.
@@
 \subsection{User Perspective}
-In describing the \tw \  user experience, we are faced with the very issue that motivated \tw \  development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to \textit{use} a system.
+In describing the \tokenWord \  user experience, we are faced with the very issue that motivated \tokenWord \  development in the first place:  descriptions in words and pictures do not give us a true sense of what it is like to \textit{use} a system.
 Since this paper's focus is on a real-world implementation and not just an abstract description, we encourage readers to visit \texttt{http://hypertext.sf.net/token\_word} to try our system for themselves.
 
-From the end-user's perspective, \tw \  has many sal\-ient features.
-Users access \tw \  with a web browser, and they must create accounts and log in to use the system.  
+From the end-user's perspective, \tokenWord \  has many sal\-ient features.
+Users access \tokenWord \  with a web browser, and they must create accounts and log in to use the system.  
 The central elements of the system are documents, which can contain quotes of other documents.
@@
 Each document also features a list of documents that quote it, so references can be followed in both directions.
-The \tw \   document display interface can be seen in Figure \ref{fig:mainScreen}.
+The \tokenWord \  document display interface can be seen in Figure \ref{fig:mainScreen}.
 
@@
 
-Figures \ref{fig:extractQuote} through \ref{fig:docPreview} show a sequence of actions from a common usage scenareo:  extracting a quote, viewing the quote on the clipboard, creating a new document that uses the quote, and previewing the document.
-After correcting the spelling mistake highlithed in Figure \ref{fig:docPreview}, the final step would be to submit the document.
-Once submitted, the work becomes a full-fledged \tw \  document, making it readable and quotable by other users in the system.
+Figures \ref{fig:extractQuote} through \ref{fig:docPreview} show a sequence of actions from a common usage scenario:  extracting a quote, viewing the quote on the clipboard, creating a new document that uses the quote, and previewing the document.
+After correcting the spelling mistake highlighted in Figure \ref{fig:docPreview}, the final step would be to submit the document.
+Once submitted, the work becomes a full-fledged \tokenWord \  document, making it readable and quotable by other users in the system.
 
 Each user has a token balance, where one token is worth one character.
-The current exchange rate is 1,000,000 tokens for \$1, and Paypal is integrated for token deposits and withdrawls.
+The current exchange rate is 1,000,000 tokens for \$1, and PayPal is integrated for token deposits and withdrawls.
 When a reader views a document that contains as of yet unviewed text regions, tokens are transfered from the reader to the original authors of the regions.
@@
 \epsfig{file=images/docPreview.eps, width=20pc}
-\caption{The document preview interface.  Quotes are expanded, and possible spelling mistakes are highlighed.}
+\caption{The document preview interface.  Quotes are expanded, and possible spelling mistakes are highlighted.}
 \label{fig:docPreview}
@@
 Full text searches are supported across the entire document space, and search terms are highlighted when result documents are displayed.
-Search results (and other lists in \tw) are sorted with most-quoted documents first, since frequently quoted documents are likely to contain the best information.
+Search results (and other lists in \tokenWord) are sorted with most-quoted documents first, since frequently quoted documents are likely to contain the best information.
 This ranking mechanism is similar to Google's PageRank algorithm \cite{Brin1998}.
 
-\tw \  provides no explicit document linking mechanism.
+\tokenWord \  provides no explicit document linking mechanism.
 However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
@@
 \epsfig{file=images/quotesAsLinks.eps, width=20pc}
-\caption{Brief portions of documents can be quoted to emulate links.  Here, the titles of two documents, ``frequently asked questions'' and ``\tw \  history,'' have been quoted.}
+\caption{Brief portions of documents can be quoted to emulate links.  Here, the titles of two documents, ``frequently asked questions'' and ``\tokenWord \  history,'' have been quoted.}
 \label{fig:quotesAsLinks}
@@
 \subsubsection{Data Model}
-Keeping with the Xanadu model, \tw \  separates documents from the text they contain.
-There are two types of data objects in \tw:  documents and chunks.
+Keeping with the Xanadu model, \tokenWord \  separates documents from the text they contain.
+There are two types of data objects in \tokenWord:  documents and chunks.
 A chunk contains a raw block of contiguous text, while a document is a list of references to text chunks.
@@
 \subsubsection{Development}
-The entire \tw \   system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
-Perl's built-in support for regular expressions was useful for the rather complicated text processing done by \tw.
+The entire \tokenWord \   system is implemented as a single CGI script written in Perl, though the script is broken up into eight modules for organization purposes.
+Perl's built-in support for regular expressions was useful for the rather complicated text processing done by \tokenWord.
 Many of these text processing operations can be expressed in succinct and elegant ways using Perl.
@@
 
-User interfaces can be layed out easily with HTML, and CGI processing is well-supported by existing Perl modules.
+User interfaces can be laid out easily with HTML, and CGI processing is well-supported by existing Perl modules.
 The CGI model requires a stateless action-response programming style, which makes it easy to focus on one feature at a time during development.
@@
 Even though the full development cycle was short, we used an iterative process.
-Features were added one at a time to \tw, and the system was maintained in a usable form at all times.
+Features were added one at a time to \tokenWord, and the system was maintained in a usable form at all times.
 For example, we started with a system that managed text chunks, then added document management, then added quotes, and then added tokens transfers.
@@
 A second approach would be to implement a simple application-level virtual filesystem for chunk and document storage.
-With this approach, we could taylor the storage system to our specific needs, though its development would certainly be labor-intensive.
+With this approach, we could tailor the storage system to our specific needs, though its development would certainly be labor-intensive.
 
-All filesystem operations in \tw \  are wrapped by a single module with only a handful of interface functions.
-By modifying the implementation of these module functions, either of the scalable backends mentioned above could be added to \tw \  with no changes to the rest of the code.
+All filesystem operations in \tokenWord \  are wrapped by a single module with only a handful of interface functions.
+By modifying the implementation of these module functions, either of the scalable backends mentioned above could be added to \tokenWord \  with no changes to the rest of the code.
 
@@
 \section{Micropayment Issues}
-With our micropyament system, we wanted to leverage PayPal's \cite{paypal} immense popularity and familiarity.
+With our micropayment system, we wanted to leverage PayPal's \cite{paypal} immense popularity and familiarity.
 By handling real-world currency exclusively through PayPal, instead of through our own virtual money system, we can process payments in a secure and trustworthy fashion.
 
-However, PayPal's currency model does not support the microdollar resolution that we need, so we cannot rely on this service alone for transfering tokens between users.
+However, PayPal's currency model does not support the microdollar resolution that we need, so we cannot rely on this service alone for transferring tokens between users.
 Even if PayPal did support high-resolution payments, it does not allow a third party to initiate transfers between account holders in a transparent and frictionless way (and for good reason, given the security issues).
@@
 To deal with these issues, we built an internal token balance system and used PayPal integration only for deposits and withdrawls of real-world currency.
-With this configuration, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tw \  documents.
+With this configuration, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tokenWord \  documents.
 Similarly, withdrawing tokens in exchange for real-world currency is not frictionless: 
-PayPal does not support an automated payment mechanism, so withdrawl requests must be queued for manual processing by the \tw \  system administrator.
+PayPal does not support an automated payment mechanism, so withdrawl requests must be queued for manual processing by the \tokenWord \  system administrator.
 Whereas deposits take effect immediately (using PayPal's ``Instant Payment Notification'' service), withdrawn token refunds are delayed by the response of the human administrator.
@@
 \subsection{Balancing Risk}
-Given that micropayments in \tw \  are mandatory and automatic, a major barrier to system adoption might exist:  trying \tw \  would require the deposit of real-world currency.
-Even the main page displayed after login is a first-class \tw \  document, so a new user with no tokens would not even be able to read a description of \tw, let alone try any of its features.
+Given that micropayments in \tokenWord \  are mandatory and automatic, a major barrier to system adoption might exist:  trying \tokenWord \  would require the deposit of real-world currency.
+Even the main page displayed after login is a first-class \tokenWord \  document, so a new user with no tokens would not even be able to read a description of \tokenWord, let alone try any of its features.
 
 One way of dealing with this adoption barrier would be to give each new user a small number of ``free'' tokens to start with (for example, at least enough tokens to read the main page).
-This solution would allow new users to try the system with no monetary investment, but it carries an enormous risk for the \tw \  system administrators.
+This solution would allow new users to try the system with no monetary investment, but it carries an enormous risk for the \tokenWord \  system administrators.
 A small group of users could create many fake accounts and then use each account to read a large dummy document owned by one user.
-This kind of scam could be used to consolodate the free starting tokens from many accounts into one account, and then a withdrawl could be made in exchange for a large amount of real-world currency.
-Even if users are not trying to intentially scam the system, doling out free tokens poses considerable risk.
-One user might write documents that are popular with new users (for example, a collection of how-to documents) and ammass a large number of free tokens over time---the withdrawl of these tokens could financially devastate the \tw \  administrators.
+This kind of scam could be used to consolidate the free starting tokens from many accounts into one account, and then a withdrawl could be made in exchange for a large amount of real-world currency.
+Even if users are not trying to intentionally scam the system, doling out free tokens poses considerable risk.
+One user might write documents that are popular with new users (for example, a collection of how-to documents) and amass a large number of free tokens over time---the withdrawl of these tokens could financially devastate the \tokenWord \  administrators.
 
@@
 The second type of tokens, called \textit{real} tokens, can be exchanged for real-world currency.
-The token transfer logic in \tw \  keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
+The token transfer logic in \tokenWord \  keeps track of token types:  trial tokens can only be transfered between users' trial balances, and real tokens can only be transfered between real balances.
 Trial tokens are favored, and real tokens are only spent when a user has no trial tokens.
@@
 \end{center}
-Suppose that user $A$ reads a new 100-chracter document that is owned by $B$, but that the document contains a 20-character quote by $C$.
+Suppose that user $A$ reads a new 100-character document that is owned by $B$, but that the document contains a 20-character quote by $C$.
 User $A$ must pay 100 tokens to access this new content, with 80 going to $B$ and 20 going to $C$.
-The transfer logic favors trial tokens, so $A$'s trial balance is exhausted first by transfering 50 tokens to $B$.
+The transfer logic favors trial tokens, so $A$'s trial balance is exhausted first by transferring 50 tokens to $B$.
 The remaining payment to $B$ is made with 30 real tokens, and 20 real tokens are also transfered to $C$.
@@
 
-This two-type scheme allows users to try \tw \  extensively without a monetary investment, and it also poses no financial risks to the administrators.
-Note that though trial tokens have no real-world value, they still have value in \tw, since they can always be used to purchase new content.
-Inside \tw, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
-A user that actively publishes popular content in \tw \  could effectively use the system forever without depositing any real-world money.
+This two-type scheme allows users to try \tokenWord \  extensively without a monetary investment, and it also poses no financial risks to the administrators.
+Note that though trial tokens have no real-world value, they still have value in \tokenWord, since they can always be used to purchase new content.
+Inside \tokenWord, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
+A user that actively publishes popular content in \tokenWord \  could effectively use the system forever without depositing any real-world money.
 
@@
 
-In terms of implementation, \tw \  is closely related to a recent class of hypertext systems known as Wikis, which are often implemented as Perl-based CGI programs.
+In terms of implementation, \tokenWord \  is closely related to a recent class of hypertext systems known as Wikis, which are often implemented as Perl-based CGI programs.
 Wikis are reader-edited web sites, and web-based HTML forms are used as the interface for page authoring.
@@
 
-%\tw \  differs from a Wiki in its approach to hypertext, since a \tw \  quote can only be taken from an existing document.
-%No mechanism is provided for refering to a document that does not yet exist.
+%\tokenWord \  differs from a Wiki in its approach to hypertext, since a \tokenWord \  quote can only be taken from an existing document.
+%No mechanism is provided for referring to a document that does not yet exist.
 
@@
 \subsection{Everything2}
-Like \tw \  and Wikis, Everything2 \cite{Everything2} is a web-based hypertext system implemented using CGI and Perl.
+Like \tokenWord \  and Wikis, Everything2 \cite{Everything2} is a web-based hypertext system implemented using CGI and Perl.
 Everything2 supports dangling links to pages that do not exist yet, but it handles these links differently than a Wiki does.
-When a user follows a dangling link, a search is performed for the title words of the non-existant page.
-Thus, dangling links are more fuctional in Everything2 from a reader's point of view.
+When a user follows a dangling link, a search is performed for the title words of the non-existent page.
+Thus, dangling links are more functional in Everything2 from a reader's point of view.
 Using this comparison point, we might conclude that Wikis favor authors, while Everything2 favors readers.
@@
 \subsection{Commonalities and Differences}
-All three systems discussed above share several features in common with \tw.
+All three systems discussed above share several features in common with \tokenWord.
 First, they are all web-based, collaborative information spaces.
@@
 
-Of course, out of all of the collaborative information spaces discussed here, \tw \  is the only system that supports deep content reuse and frictionless micropayments.
+Of course, out of all of the collaborative information spaces discussed here, \tokenWord \  is the only system that supports deep content reuse and frictionless micropayments.
 Thus, these systems are closely related in terms of implementation, but their goals and end-user experiences are very different.
@@
 \section{Conclusion}
-Thoughout this paper, we have discussed the strategies that made \tw \  development possible, including an iterative process and heavy use of existing technology.
+Throughout this paper, we have discussed the strategies that made \tokenWord \  development possible, including an iterative process and heavy use of existing technology.
 
@@
 
-\tw \  is by no means an ideal xanalogical system, and many features are missing.
+\tokenWord \  is by no means an ideal xanalogical system, and many features are missing.
 However, it is still the first system to implement the core features of the Xanadu architecture.
-Though one would be hard-pressed to argue that the features included in \tw \  are not crucial, three important features are missing.
-First, \tw \  does not explicitly support document versioning.
+Though one would be hard-pressed to argue that the features included in \tokenWord \  are not crucial, three important features are missing.
+First, \tokenWord \  does not explicitly support document versioning.
 However, using the quotation primitive, a limited form of versioning can be emulated (a user can quote unchanged regions of the previous version when creating a new version).
-Second, \tw \  does not support multi-server integration:  each installation of \tw \  operates in isolation, and quotes between documents at different sites are not possible.
+Second, \tokenWord \  does not support multi-server integration:  each installation of \tokenWord \  operates in isolation, and quotes between documents at different sites are not possible.
 We see multi-server integration as one of the weakpoints in the Xanadu architecture:  how can we ensure that references never break in a system comprised of multiple, separately owned servers?
 Even if fault-tolerant, multi-server integration is possible, it is not essential for the end-user experience. 
-Third, \tw \   does not support side-by-side document comparission with \textit{transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
+Third, \tokenWord \   does not support side-by-side document comparison with \textit{transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
 The transpointing interface would be difficult, if not impossible, to support in a web browser with no additional software.
-However, a side-by-side document comparisson interface, using colored highlighting to indicate itentical regions, has been contemplated for \tw.
+However, a side-by-side document comparison interface, using colored highlighting to indicate identical regions, has been contemplated for \tokenWord.
 Implementing such an interface would be easy, though coming up with a highlighting scheme that works correctly in the general case (for example, without running out of readable colors) is quite difficult.
@@
 For example, a presentation layer could specify font sizes, links, or annotations, and multiple layers could be stacked when rendering a particular piece of content.
-Given \tw's current data model and presentation logic, adding layers would not be difficult.
+Given \tokenWord's current data model and presentation logic, adding layers would not be difficult.
 In fact, particular types of layers are already implemented:  highlights for misspellings, quote context, and hit search terms are applied to document text after it is assembled.

### 2003-02-15 papers/hypertext2003/paper.tex
Finished final round of proof reading.

@@
 % Spell-checked.
+% Finished final round of proof reading.
 %
@@
 To our knowledge, \tokenWord \  is the first xanalogical system implementation to included all of these features.
-Furthermore, \tokenWord \  is the first xanalogical system of any kind to be accessible by a web browser with no additional software.
+Furthermore, \tokenWord \  is the first xanalogical system of any kind to be accessible using a web browser with no additional software.
 Previous attempts at full xanalogical implementations took many years and were ultimately never completed.
@@
 Xanadu is a dream and an ideal.  
-We know it would be great (or at least interesting) if a xanalogical system existed, but we are also resigned to the notion that such a system will probably never exist.
+We know that it would be great (or at least interesting) if a xanalogical system existed, but we are also resigned to the notion that such a system will probably never exist.
 Is Xanadu impossible?
@@
 
-Transclusion creates a serious problem, at least in combination with how we commonly interact with electronic documents.
-Electronic documents change constantly.
+Transclusion creates a serious problem, at least in combination with how we commonly interact with electronic documents:  they change constantly.
 If $B$ changes or is deleted, $A$'s quote can break.
@@
 Though reading content requires payment, quoting is essentially free, since the content is not accessed during the act of quoting.
-In practice, an author will need to read a document before quoting it, but this reading requires only the normal first-access payment, no matter how widely the new, quoting document is expected to be read.
+In practice, an author will need to read a document before quoting from it, but this reading requires only the normal first-access payment, no matter how widely the new, quoting document is expected to be read.
 However, the more a document is quoted and read in quoted form, the more micropayments the original author will receive.
@@
 
-Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
-To extract a document region as a quote, the user inserts $<$\texttt{q}$>$ $<$$/$\texttt{q}$>$ tags around the desired region in a text area.
-This interaction mechanism is arguably more elegant and less error-prone than mouse-based selection highlighting, especially when extracting large regions that span several screens full of text.
-Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
-Each quote is assigned a $<$\texttt{q N}$>$ tag to be used when inserting the quote into new documents---$<$\texttt{q 3}$>$ refers to the quote at index three on the clipboard.
-The use of these abreviated handles hides the complexity of references and document regions from the user.
-After extracting a quote, the user never needs to deal directly with the document region again, though the original context of a quote can be seen with a single click from the quote clipboard.
-The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
-When creating a new document, a user can enter new text along with handle tags for quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
-A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.
-
 \begin{figure}[t]
@@
 \end{figure}
+
+Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
+To extract a document region as a quote, the user inserts $<$\texttt{q}$>$ $<$$/$\texttt{q}$>$ tags around the desired region in a text area.
+Though it was motivated by the limitations of a web-based user interface, this interaction mechanism is arguably more elegant and less error-prone than mouse-based selection highlighting, especially when extracting large regions that span several screens full of text.
+Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
+Each quote is assigned a $<$\texttt{q N}$>$ tag to be used when inserting the quote into new documents---$<$\texttt{q 3}$>$ refers to the quote at index three on the clipboard.
+The use of these abreviated handles hides the complexity of references and document regions from the user.
+After extracting a quote, the user never needs to deal directly with the document region again, though the original context of a quote can be accessed from the clipboard with a single click.
+The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
+When creating a new document, a user can enter new text along with handle tags for quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
+A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.
 
@@
 Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.
-
-Each reference in a document contains a pointer to a text chunk region and an optional pointer to a document context region.
-The document context pointer tracks which document the material was quoted from and is used for quote reference chasing.
-If a document refers to a new text chunk that has not appeared in any previous documents, the document context pointer is omitted:  such chunks are not part of quotes and have no references that can be chased.
-With this two-pointer model, we can distinguish ``original'' material in a document from quoted material.  % and support recursive reference chasing.
-By following references recursively for a nested quotation, the original author and document context of particular words can be obtained.
-%When following a quote reference, a chain of references may need to be chased before the original context of the text is found.
 
@@
 \end{figure*}
+
+Each reference in a document contains a pointer to a text chunk region and an optional pointer to a document context region.
+The document context pointer tracks which document the material was quoted from and is used for quote reference chasing.
+If a document refers to a new text chunk that has not appeared in any previous documents, the document context pointer is omitted:  such chunks are not part of quotes and have no references that can be chased.
+With this two-pointer model, we can distinguish ``original'' material in a document from quoted material.  % and support recursive reference chasing.
+By following references recursively for a nested quotation, the original author and document context of particular words can be obtained.
+%When following a quote reference, a chain of references may need to be chased before the original context of the text is found.
 
@@
 Even though the full development cycle was short, we used an iterative process.
-Features were added one at a time to \tokenWord, and the system was maintained in a usable form at all times.
+Features were added to \tokenWord \  one by one, and the system was maintained in a usable form at all times.
 For example, we started with a system that managed text chunks, then added document management, then added quotes, and then added tokens transfers.
@@
 The Xanadu model is complex and subtle, and it is easy to get bogged down by details without ever producing a working system.
-Our system started out simple and grew in complexity, feature by feature.
+Our system started out simple and grew in complexity, one feature at a time.
 
@@
 In our live system, we chose an exchange rate of 1,000,000 tokens for \$1, though this parameter can be changed on a site-by-site basis.
-With this exchange rate, we tried to minimize financial burden on readers while still assigning appreciable value to content.
+With this exchange rate, we tried to minimize the financial burden on readers while still assigning appreciable value to content.
 For example, the full text of this paper would cost about \$0.04, so 25 people would need to read it before it earned \$1 worth of tokens.
@@
 Links can be created to documents that do not yet exist without knowing where those documents will eventually reside.
-To create a new document, a user must follow one of these dangling links in an existing page, which leads to a page creation screen.
+To create a new document, a user must follow one of these dangling links in an existing page---this action leads to a page creation screen.
 Thus, in a Wiki, there is no way to create a page in isolation.
@@
 Even if fault-tolerant, multi-server integration is possible, it is not essential for the end-user experience. 
-Third, \tokenWord \   does not support side-by-side document comparison with \textit{transpointing} lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
+Third, \tokenWord \   does not support side-by-side document comparison with transpointing lines, a classic Xanadu interface feature that Nelson's recent paper describes in detail \cite{Nelson1999}.
 The transpointing interface would be difficult, if not impossible, to support in a web browser with no additional software.
@@
 ``Xanadu'' is a trademark of Ted Nelson.
-To prevent confusion, the generic terms (\textit{e.g.}, xanalogical system) have been used wherever possible.
+To prevent confusion, the generic terms (\textit{e.g.}, xanalogical system) have been used whenever possible.
 

### 2003-04-01 papers/hypertext2003/paper.tex
Fixed a typo.

@@
 % Finished final round of proof reading.
+%
+% -- First round hypertext 2003 submission happened here --
+%
+% 2003-April-1 Jason Rohrer
+% Fixed a typo.
 %
@@
 \subsection{Weblogs}
-Another class of related web based hypertext systems are weblogs, or ``blogs.''
+Another class of related web-based hypertext systems are weblogs, or ``blogs.''
 These systems allow content to be added to a web site serially, one post at a time.

### 2003-04-01 papers/hypertext2003/paper.tex
Fixed mistakes pointed out by Nelson. Added comments for Nelson's suggestions.

@@
 % Fixed a typo.
+% Fixed mistakes pointed out by Nelson.  
+% Added comments for Nelson's suggestions.
 %
@@
 In 1992, after four years of development and \$5 million spent \cite{AutodeskCost},  Autodesk ceased development of Xanadu \cite{AutodeskPressDrop}.
+% Add reasons here?  Factional disputes, restarts with a fresh code base, etc.
 Ironically, this decision was made just when the world was ripe for the first global hypertext system \cite{BernersLee92}.
@@
 Each user has a token balance, where one token is worth one character.
-The current exchange rate is 1,000,000 tokens for \$1, and PayPal is integrated for token deposits and withdrawls.
+The current exchange rate is 1,000,000 tokens for \$1, and PayPal is integrated for token deposits and withdrawals.
 When a reader views a document that contains as of yet unviewed text regions, tokens are transfered from the reader to the original authors of the regions.
@@
 
-\tokenWord \  provides no explicit document linking mechanism.
+The \tokenWord \  system provides no explicit document linking mechanism.
 However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
@@
 
-We chose a filesystem backend, despite its scalability limitations, because of its simplicity.
+We chose a directory tree backend, despite its scalability limitations, because of its simplicity.
 This choice fits into our implementation philosophy, since the focus was on producing a working system and adding features iteratively.
@@
 
-To deal with these issues, we built an internal token balance system and used PayPal integration only for deposits and withdrawls of real-world currency.
+To deal with these issues, we built an internal token balance system and used PayPal integration only for deposits and withdrawals of real-world currency.
 With this configuration, a deposit is by no means frictionless (logging in to PayPal is required), but after the deposit has been made, token payments are completely transparent as the user accesses \tokenWord \  documents.
 Similarly, withdrawing tokens in exchange for real-world currency is not frictionless: 
-PayPal does not support an automated payment mechanism, so withdrawl requests must be queued for manual processing by the \tokenWord \  system administrator.
+PayPal does not support an automated payment mechanism, so withdrawal requests must be queued for manual processing by the \tokenWord \  system administrator.
 Whereas deposits take effect immediately (using PayPal's ``Instant Payment Notification'' service), withdrawn token refunds are delayed by the response of the human administrator.
-From the administrator's point of view, the withdrawl queue can be used to increase security, since any suspicious activity can be investigated before real-world payments are made.
+From the administrator's point of view, the withdrawal queue can be used to increase security, since any suspicious activity can be investigated before real-world payments are made.
 
@@
 A small group of users could create many fake accounts and then use each account to read a large dummy document owned by one user.
-This kind of scam could be used to consolidate the free starting tokens from many accounts into one account, and then a withdrawl could be made in exchange for a large amount of real-world currency.
+This kind of scam could be used to consolidate the free starting tokens from many accounts into one account, and then a withdrawal could be made in exchange for a large amount of real-world currency.
 Even if users are not trying to intentionally scam the system, doling out free tokens poses considerable risk.
-One user might write documents that are popular with new users (for example, a collection of how-to documents) and amass a large number of free tokens over time---the withdrawl of these tokens could financially devastate the \tokenWord \  administrators.
+One user might write documents that are popular with new users (for example, a collection of how-to documents) and amass a large number of free tokens over time---the withdrawal of these tokens could financially devastate the \tokenWord \  administrators.
 
@@
 However, we should mention that interest in Xanadu has not waned in recent years, even though development work on Udanax, the last official (and most ambitious) Xanadu implementation effort, ceased in 1995 \cite{Udanax}.
+% Two code bases, Green which stopped in 1988, and Gold which stopped in 1995
+% Still worked on sporadically by enthusiasts.
 For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
@@
 
-\tokenWord \  is by no means an ideal xanalogical system, and many features are missing.
+The \tokenWord \  architecture is by no means an ideal xanalogical system, and many features are missing.
 However, it is still the first system to implement the core features of the Xanadu architecture.

### 2019-09-01 papers/hypertext2003/samplePaper/sigproc-sp.tex

% This is sigproc-sp.tex -FILE FOR V2.6SP OF ACM_PROC_ARTICLE-SP.CLS
% OCTOBER 2002
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V2.6SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.6SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
%
%  However, both the CopyrightYear (default to 2002) and the ACM Copyright Data
% (default to X-XXXXX-XX-X/XX/XX) can still be over-ridden by whatever the author
% inserts into the source .tex file.
% e.g.
% \CopyrightYear{2003} will cause 2003 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@acm.org
%
% For tracking purposes - this is V2.6SP - OCTOBER 2002

\documentclass{../acm_proc_article-sp}

\begin{document}
%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\setpagenumber{50}
%\CopyrightYear{2002} % Allows default copyright year (2002) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (X-XXXXX-XX-X/XX/XX) to be over-ridden.
% --- End of Author Metadata ---

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the permission block, copyright information and page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS V2.6SP. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the "boxing"
% and alignment of the authors under the title, and to add
% a section for authors number 4 through n.
%
% Up to the first three authors are aligned under the title;
% use the \alignauthor commands below to handle those names
% and affiliations. Add names, affiliations, addresses for
% additional authors as the argument to \additionalauthors;
% these will be set for you without further effort on your
% part as the last section in the body of your article BEFORE
% References or any Appendices.

\numberofauthors{5}
%
% You can go ahead and credit authors number 4+ here;
% their names will appear in a section called
% "Additional Authors" just before the Appendices
% (if there are any) or Bibliography (if there
% aren't)

% Put no more than the first THREE authors in the \author command
\author{
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
%% e-mail address with \email.
\alignauthor Ben Trovato\titlenote{Dr.~Trovato insisted his name
be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
\alignauthor G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
}
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Delphi theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\begin{figure}
\centering
\psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the \texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.

% That's all folks!
\end{document}

### 2019-09-01 tokenWord.pl
Remove tokenWord_errors.log, use STDERR instead
closes #2

@@ -2,9 +2,6 @@
 
 #!/usr/bin/perl -wT
 
-
-
-
 #
 # Modification History
 #
@@ -87,24 +84,13 @@
 # 2004-December-3   Jason Rohrer
 # Added inline image support.
 #
-
-
-
-# setup a local error log
-use CGI::Carp qw(carpout);
-BEGIN {
-    use CGI::Carp qw(carpout);
-    open(LOG, ">>./tokenWord_errors.log") or
-        die("Unable to open tokenWord_errors.log: $!\n");
-    carpout(LOG);
-}
-
-
+# 2019-September-1   Jakob Voß
+# Remove tokenWord_errors.log, use STDERR instead
 
 use lib '.';
 
 use strict;
-use CGI;                # Object-Oriented
+use CGI;    # Object-Oriented
 use MD5;
 
 use tokenWord::common;
@@ -119,95 +105,87 @@ use tokenWord::htmlGenerator;
 
 use Time::HiRes;
 
-
 my $paypalPercent = 0.029;
-my $paypalFee = 0.30;
-# my $paypalNotifyIP = "65.206.229.140";   # IP of notify.paypal.com
-# New IP as of June 11, 2004 
-my $paypalNotifyIP =           "216.113.188.202";
+my $paypalFee     = 0.30;
 
+# my $paypalNotifyIP = "65.206.229.140";   # IP of notify.paypal.com
+# New IP as of June 11, 2004
+my $paypalNotifyIP = "216.113.188.202";
 
 # allow group to write to our data files
-umask( oct( "02" ) );
+umask( oct("02") );
 
 # make sure data directories exist
 setupDataDirectory();
-
-
-
 
 my $cgiQuery = CGI->new();
 
 # always set the Pragma: no-cache directive
 # this feature seems to be undocumented...
-$cgiQuery->cache( 1 );
+$cgiQuery->cache(1);
 
-
-my $action = $cgiQuery->param( "action" ) || '';
-
-
+my $action = $cgiQuery->param("action") || '';
 
 # get the cookie, if it exists
-my $userCookie = $cgiQuery->cookie( "loggedInUser" ) ;
-my $userSessionIDCookie = $cgiQuery->cookie( "sessionID" ) ;
-my $userShowQuotesCookie = $cgiQuery->cookie( "showQuotes" ) ;
-
+my $userCookie           = $cgiQuery->cookie("loggedInUser");
[…]
